### 2019-01-05 article/main.tex
Edge connectivity

\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{authblk}
\usepackage{booktabs}
%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{pgfplots}
\pgfplotsset{compat=1.12}
\usepackage[group-separator={,}]{siunitx}
\usepackage{amsmath}
\usepackage{wrapfig}
\usepackage{amsthm}
\usetikzlibrary{arrows,automata}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{breqn}
\usepackage{algpseudocode}
\usepackage{float}
\usepackage{tikz}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usepackage{eufrak}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage[toc,page]{appendix}
\usepackage{color}
\definecolor{lightgray}{rgb}{.9,.9,.9}
\definecolor{darkgray}{rgb}{.4,.4,.4}
\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
\floatname{algorithm}{Procedure}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

\lstdefinelanguage{JavaScript}{
	keywords={typeof, contract, struct, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
	keywordstyle=\color{blue}\bfseries,
	ndkeywords={class, export, boolean, throw, implements, import, this},
	ndkeywordstyle=\color{darkgray}\bfseries,
	identifierstyle=\color{black},
	sensitive=false,
	comment=[l]{//},
	morecomment=[s]{/*}{*/},
	commentstyle=\color{purple}\ttfamily,
	stringstyle=\color{red}\ttfamily,
	morestring=[b]',
	morestring=[b]"
}

\lstset{
	language=JavaScript,
	backgroundcolor=\color{lightgray},
	extendedchars=true,
	basicstyle=\footnotesize\ttfamily,
	showstringspaces=false,
	showspaces=false,
	numbers=left,
	numberstyle=\footnotesize,
	numbersep=9pt,
	tabsize=2,
	breaklines=true,
	showtabs=false,
	captionpos=b
}

\usepackage{graphicx}
\usepackage[
n,
operators,
advantage,
sets,
adversary,
landau,
probability,
notions,	
logic,
ff,
mm,
primitives,
events,
complexity,
asymptotics,
keys]{cryptocode}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\newcommand{\Mod}[1]{\ (\mathrm{mod}\ #1)}

\def\bitcoinA{%
	\leavevmode
	\vtop{\offinterlineskip %\bfseries
		\setbox0=\hbox{B}%
		\setbox2=\hbox to\wd0{\hfil\hskip-.03em
			\vrule height .3ex width .15ex\hskip .08em
			\vrule height .3ex width .15ex\hfil}
		\vbox{\copy2\box0}\box2}}

\DeclareMathOperator{\EX}{\mathbb{E}}% expected value
\providecommand{\keywords}[1]{\textbf{\textit{Keywords:}} #1}

\renewcommand{\lstlistingname}{Figure}% Listing -> Algorithm
\renewcommand{\lstlistlistingname}{List of \lstlistingname s}% List of Listings -> List of Algorithms

\newcommand{\smallsim}{\smallsym{\mathrel}{\sim}}

\makeatletter
\newcommand{\smallsym}[2]{#1{\mathpalette\make@small@sym{#2}}}
\newcommand{\make@small@sym}[2]{%
	\vcenter{\hbox{$\m@th\downgrade@style#1#2$}}%
}
\newcommand{\downgrade@style}[1]{%
	\ifx#1\displaystyle\scriptstyle\else
	\ifx#1\textstyle\scriptstyle\else
	\scriptscriptstyle
	\fi\fi
}
\makeatother

\title{Post-Quantum Verifiable Delay Functions}
\author[1]{Péter Burcsi}
\author[1]{István András Seres}
\author[1]{Dániel A. Nagy}
\affil[1]{Department of Computer Algebra, Eötvös Loránd University}
\begin{document}
\maketitle

\begin{abstract}

\end{abstract}
\keywords{Cryptography, Verifiable delay function, Post-Quantum Cryptography, Cryptocurrency, Ethereum}

\section{Introduction}
\section{Background}
\section{Construction}
\section{Security arguments}
\section{Conclusion}
\section{Acknowledgements}

\end{document}

### 2019-01-05 parseGraph.py

@@ -4,6 +4,8 @@ from pprint import pprint
 import math
 import matplotlib.pyplot as plt
 import matplotlib.colors as mcolors
+import matplotlib.ticker as mticker
+from matplotlib.ticker import MaxNLocator
 import collections
 import numpy as np
 import heapq
@@ -20,13 +22,15 @@ def main():
     #weightsDistribution(G)
     #shortestPaths(G)
     #drawGraph(G)
-    #robustness(G)
+    #vertexConnectivity(G)
+    #edgeConnectivity(G)
 
 #degreeCentrality
 
 def basicStatistics(G):
     print("Number of LN nodes : ", G.order())
     print("Number of LN payment channels: ", G.size())
+    print("Density of LN: ",nx.classes.function.density(G))
     print("Amount of BTC, denominated in Satoshis, in all payment channels:", allMoneyStaked)
     print("Number of connected components: ", len(list(nx.connected_components(G))))
     print("Maximal independent set: ", len(nx.algorithms.maximal_independent_set(G)))
@@ -47,14 +51,82 @@ def basicStatistics(G):
     #print("LN's S-metric: ", smetric(G)) #0.6879664061934981
     print("LN average clustering coefficient", approximation.clustering_coefficient.average_clustering(G))
     #print("LN's largest clique size: ", nx.algorithms.approximation.clique.max_clique(G))
+    # Betweenness centrality
+    print("Betweenness-centrality: ", nx.algorithms.centrality.betweenness_centrality(G))
+    # Closeness centrality
+    #clo_cen = nx.closeness_centrality(cam_net_mc)
+    # Eigenvector centrality
+    #eig_cen = nx.eigenvector_centrality(cam_net_mc)
 
-def robustness(G):
-    G.remove_nodes_from(list(nx.connected_components(G))[1])  # there is a small second component
+def vertexConnectivity(G):
     sortedNodes = sorted(G.degree(), key=lambda x: x[1], reverse=True)
+    comp=[0]
+    cnt=[2]
     print("what?",len(list(nx.connected_components(G))))
     for x in range(30):
         G.remove_node(sortedNodes[x][0])
+        comp.append(x+1)
+        cnt.append(len(list(nx.connected_components(G))))
         print(x+1,len(list(nx.connected_components(G))))
+
+    fig, ax = plt.subplots()
[…]

### 2019-01-06 article/main.tex
Random failures

@@
 
-\title{Post-Quantum Verifiable Delay Functions}
-\author[1]{Péter Burcsi}
+\title{Topological Analysis of Bitcoin's Lightning Network }
 \author[1]{István András Seres}
 \author[1]{Dániel A. Nagy}
+\author[1]{Péter Burcsi}
 \affil[1]{Department of Computer Algebra, Eötvös Loránd University}
@@
 \end{abstract}
-\keywords{Cryptography, Verifiable delay function, Post-Quantum Cryptography, Cryptocurrency, Ethereum}
+\keywords{Bitcoin, Lightning Network, Network Topology, Payment Channel Network}
 
 \section{Introduction}
-\section{Background}
-\section{Construction}
-\section{Security arguments}
+\section{Lightning Network's Topology}
+\section{Robustness of LN}
+\subsection{Random Failures}
+\subsection{Targeted attacks}
+\begin{figure}[h]
+	\centering
+	\begin{minipage}{.5\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{vertexConnectivity.png}
+		\captionof{figure}{LN's vertex connectivity}
+		\label{fig:test1}
+	\end{minipage}%
+	\begin{minipage}{.5\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{edgeConnectivity.png}
+		\captionof{figure}{LN's edge connectivity}
+		\label{fig:test2}
+	\end{minipage}
+\end{figure}
+
+\subsection{Fixing LN's resilience against attacks}
+percolation threshold
+\section{Privacy}
+topological anomalies have privacy implications, low usage of tor, even tor can not help
 \section{Conclusion}

### 2019-01-06 parseGraph.py

@@ -8,6 +8,7 @@ import matplotlib.ticker as mticker
 from matplotlib.ticker import MaxNLocator
 import collections
 import numpy as np
+from random import randint
 import heapq
 from networkx.algorithms import approximation
 
@@ -17,15 +18,19 @@ allWeights = []
 
 def main():
     G=defineGraph(readFile())
-    basicStatistics(G)
-    #degreeDistribution(G)
+    #basicStatistics(G)
+    #degreeDistribution(G) #percentile graph needs to be added
     #weightsDistribution(G)
     #shortestPaths(G)
     #drawGraph(G)
     #vertexConnectivity(G)
     #edgeConnectivity(G)
+    randomVertexConnectivity(G)
+    #centrality(G)
+    #clusteringCoefficient(G)
 
 #degreeCentrality
+
 
 def basicStatistics(G):
     print("Number of LN nodes : ", G.order())
@@ -50,31 +55,105 @@ def basicStatistics(G):
     print("Number of isolates in LN: ", list(nx.isolates(G)))
     #print("LN's S-metric: ", smetric(G)) #0.6879664061934981
     print("LN average clustering coefficient", approximation.clustering_coefficient.average_clustering(G))
+    print("LN's transitivity: ", nx.algorithms.cluster.transitivity(G))
     #print("LN's largest clique size: ", nx.algorithms.approximation.clique.max_clique(G))
-    # Betweenness centrality
-    print("Betweenness-centrality: ", nx.algorithms.centrality.betweenness_centrality(G))
-    # Closeness centrality
-    #clo_cen = nx.closeness_centrality(cam_net_mc)
-    # Eigenvector centrality
-    #eig_cen = nx.eigenvector_centrality(cam_net_mc)
+    #81 onion node :(
+
+def clusteringCoefficient(G):
+    sortedNodes = sorted(G.degree(), key=lambda x: x[1], reverse=True)
+    print(sortedNodes[0][0])
+    highDegreeNodes = []
+    for x in range(30):
+        highDegreeNodes.append(sortedNodes[x][0])
+
+    clusteringCoefficients=nx.algorithms.cluster.clustering(G)
+    valueArr = []
+    for key,value in clusteringCoefficients.items():
+        valueArr.append(value)
+        print(value)
+    binwidth = 0.01
+    plt.hist(valueArr, bins=np.arange(min(valueArr), max(valueArr) + binwidth, binwidth))
+
[…]

### 2019-01-06 article/main.tex
Started writing

@@
 \usepackage{authblk}
+\usepackage[export]{adjustbox}
 \usepackage{booktabs}
+\usepackage{ae,aecompl}
 %% Sets page size and margins
@@
 \begin{abstract}
-
+Bitcoin's Lightning Network (LN) is a scalability solution for Bitcoin, which allows transactions to be issued with negligible fees and settle transactions instantly at scale.
+In order to use LN funds need to be locked in payment channels on the Bitcoin blockchain (Layer-1), that one may use them in LN (Layer-2).
+LN is comprised of many payment channels forming a payment channel network.
+A few payment channels already enable anyone to efficiently, securely and privately route payments across the whole network.
+In this paper we argue that LN's current topological properties largely harms its value proposition and potential.
 \end{abstract}
@@
 \section{Introduction}
+Recently the Bitcoin \cite{nakamoto2008bitcoin} network celebrated its 10th anniversary.
+During these years Bitcoin gained a huge popularity due to its publicly verifiable, decentralized, permissionless and censorship-resistant nature.
+This tremendous popularity and increasing interest in Bitcoin pushed its network's throughput to its limits.
+Without further advancements, the Bitcoin network can only settle $7$ transactions per second (tps), while mainstream centralized payment providers such as Visa and Mastercard can process approximately \num[group-separator={,}]{40000} tps in peak hours.
+Moreover one might need to pay large transaction fees on the Bitcoin network, while also need to wait 6 new blocks to be published in order to be certain enought that the transaction is included in the blockchain.
+
+To alleviate these scalability issues the Lightning Network (LN) is designed in 2016 \cite{poon2016bitcoin}, and launched in 2018, January.
+The main insight of LN is that transactions can be issued also off-blockchain in a trust-minimized manner achieving instant transaction confirmation times with negligible fees, whilst retaining the security of the underlying blockchain.
+
+Bidirectional payment channels can be formed on-chain using a construction called Hashed Timelock Contracts (HTLC).
+Later several payments can take place in a payment channel.
+The main advantage of payment channels is that one can send and receive thousands of payments with essentially only 2 on-chain transations: the opening and closing channel transactions.
+
+Using these payment channels as building blocks one might establish a payment channel network, where it is not necessary to have direct payment channels between nodes to transact with each other, but they could simply route their payments through other nodes' payment channels.
+Such a network can be built, because LN achieves payments to be made without any counterparty risk, however efficient and privacy-preserving payment routing remains a challenging algorithmic task \cite{roos2017settling}.
+
+\textbf{Our contributions.} We empirically measure and describe LN's topology and show that it is utterly centralized and fragile against both random failures and targeted attacks.
+These findings suggest that LN, unlike Bitcoin, is far from being reliable, censorship-resistant, decentralized and private.
 \section{Lightning Network's Topology}
+LN can be described as a weighted graph $G=(V,E)$, where $V$ is the set of LN nodes and $E$ is the set of bidirectional payment channels between these nodes.
+We took a snapshot\footnote{https://graph.lndexplorer.com} of LN's topology on the 10th birthday of Bitcoin, 2019 January 3rd.
+In the following we are going to analyze this dataset.
+
+\begin{wrapfigure}[19]{r}{5.5cm}
+
+	\begin{tabular}{ | l | c | }
+		\hline
+		Number of nodes & $2344$  \\ \hline
+		Number of payment channels & $16617$  \\ \hline
+		Connected components & $2$  \\ \hline
+		Density & $0.00605$ \\ \hline
+		Total BTC held in LN & $543.61855$\bitcoinA\\ \hline
+		s-metric& $0.6878$ \\ \hline
+		Maximal independent set & $1564$ \\ \hline
+		Bridges & $530$ \\ \hline
+		Diameter & $6$ \\ \hline
+		Radius & $3$ \\ \hline
+		Transitivity& $0.1046$\\ \hline
+		Average clustering coefficient&$0.304$ \\ \hline
+		Degree assortativity& $-0.2690$ \\ \hline
+	\end{tabular}
+	\caption{LN at a glance: basic properties of the LN graph.}\label{fig:properties}
+\end{wrapfigure}
+
+LN gradually increased adoption and attraction throughout 2018, which resulted in 3 independent client implementations and \num[group-separator={,}]{2344} nodes joining LN as of 2019, January 3rd.
+The density of a graph is defined as $D=\frac{2\mid E\mid}{\mid V\mid \mid V-1\mid}$  which is the ratio of present and potential edges.
+As it is shown in Figure \ref{fig:properties}.
+LN is quite a parse graph.
+This is further justified by the fact that LN has \num[group-separator={,}]{530} bridges, edges which deletion increases the number of connected components.
+Although LN is consisted of $2$ components, the second component has only $3$ nodes.
+The low transitivity, fraction of present and possible triangles in the graph, highlights the sparseness of LN as well.
+
+However LN also exhibits somewhat scale-free properties as the s-metric suggests.
+S-metric was first introduced by Lun Li et al.
+in \cite{li2005towards} and defined as $s(G)=\sum_{(u,v)\in E}deg(u)deg(v)$.
+The closer to $1$  s-metric of $G$ is, the more scale-free the network.
+Diameter and radius of LN suggests that LN is a small world.
+Somewhat scale-freeness is also exhibited in the degree distribution of LN.
+Majority of nodes have very few payment channels, although there are a few hubs who have significantly more connections as it can be seen in Figure~\ref{fig:degreedist}.
+
+\begin{figure}[h]
+	\centering
+	\label{fig:degreedist}
+	\includegraphics[scale=0.4]{degreehistogramlogscale.jpg}
+	\caption{LN's degree distribution}	
+\end{figure}
+
 \section{Robustness of LN}
@@
 
+\bibliographystyle{plain}
+\bibliography{sample}
+
 \end{document}

### 2019-01-06 parseGraph.py

@@ -8,7 +8,9 @@ import matplotlib.ticker as mticker
 from matplotlib.ticker import MaxNLocator
 import collections
 import numpy as np
+import string
 from random import randint
+from random import seed
 import heapq
 from networkx.algorithms import approximation
 
@@ -18,18 +20,23 @@ allWeights = []
 
 def main():
     G=defineGraph(readFile())
-    #basicStatistics(G)
+    basicStatistics(G)
     #degreeDistribution(G) #percentile graph needs to be added
     #weightsDistribution(G)
     #shortestPaths(G)
     #drawGraph(G)
     #vertexConnectivity(G)
     #edgeConnectivity(G)
-    randomVertexConnectivity(G)
+    #randomVertexConnectivity(G)
     #centrality(G)
     #clusteringCoefficient(G)
+    #simpleStatistics(G)
 
 #degreeCentrality
+
+def simpleStatistics(G):
+    a=[22, 1, 11, 6, 5,15, 26, 15, 8, 9,47, 13, 8, 3, 12,6, 22, 7, 1, 6,44, 7, 12, 14, 4,15, 19, 4, 1, 13]
+    print(np.mean(a)/G.order())
 
 
 def basicStatistics(G):
@@ -110,22 +117,22 @@ def randomVertexConnectivity(G):
     sortedNodes = sorted(G.degree(), key=lambda x: x[1], reverse=True)
     print(len(list(nx.connected_components(G))))
     threshold=[]
-    target = 1000
+    target = 500
     Gor=[]
     sortedNodesList=[]
-    for x in range(target):
-        Gor.append(G.copy())
-        sortedNodesList.append(sortedNodes)
+    for z in range(target):
+        Gor.append(nx.Graph(G))
+        sortedNodesList.append(sorted(Gor[-1].degree(), key=lambda x: x[1], reverse=True))
 
     for y in range(target):
-        for x in range(700):
-            randomNode=randint(0, len(sortedNodesList[y])-1)
-            print(randomNode,len(sortedNodesList[y]))
+        for x in range(len(sortedNodes)):
+            randomNode=randint(0,len(sortedNodesList[y])-1)
+            #print(randomNode,len(sortedNodesList[y]))
             Gor[y].remove_node(sortedNodesList[y][randomNode][0])
             sortedNodesList[y].remove(sortedNodesList[y][randomNode])
-            if len(list(nx.connected_components(Gor[y]))) == 2:
+            if len(list(nx.connected_components(Gor[y]))) > 1:
[…]

### 2019-01-06 article/main.tex
Robustness of LN

@@
 
+\begin{wrapfigure}{r}{0.7\textwidth}
+	\begin{center}
+		\includegraphics[width=0.9\textwidth]{LNtopology.png}
+	\end{center}
+	\caption{LN's topology. Nodes with higher degree are highlighted with lighter colors}
+	\vspace{-10pt}
+\end{wrapfigure}
+
 To alleviate these scalability issues the Lightning Network (LN) is designed in 2016 \cite{poon2016bitcoin}, and launched in 2018, January.
@@
 \section{Lightning Network's Topology}
-LN can be described as a weighted graph $G=(V,E)$, where $V$ is the set of LN nodes and $E$ is the set of bidirectional payment channels between these nodes.
-We took a snapshot\footnote{https://graph.lndexplorer.com} of LN's topology on the 10th birthday of Bitcoin, 2019 January 3rd.
-In the following we are going to analyze this dataset.
-
-\begin{wrapfigure}[19]{r}{5.5cm}
-
+\begin{wrapfigure}[18]{r}{5.5cm}
 	\begin{tabular}{ | l | c | }
@@
 
+LN can be described as a weighted graph $G=(V,E)$, where $V$ is the set of LN nodes and $E$ is the set of bidirectional payment channels between these nodes.
+We took a snapshot\footnote{https://graph.lndexplorer.com} of LN's topology on the 10th birthday of Bitcoin, 2019 January 3rd.
+In the following we are going to analyze this dataset.
+
 LN gradually increased adoption and attraction throughout 2018, which resulted in 3 independent client implementations and \num[group-separator={,}]{2344} nodes joining LN as of 2019, January 3rd.
@@
 
-\begin{figure}[h]
-	\centering
-	\label{fig:degreedist}
-	\includegraphics[scale=0.4]{degreehistogramlogscale.jpg}
-	\caption{LN's degree distribution}	
-\end{figure}
+\begin{wrapfigure}{r}{0.6\textwidth}
+	\caption{LN's degree distribution}\label{fig:degreedist}
+	\begin{center}
+		\includegraphics[width=0.85\textwidth]{degreehistogramlogscale.png}
+	\end{center}	
+\end{wrapfigure}
+
+Negative degree assortativity of the graph indicates that on average low degree nodes tend to connect to high degree nodes rather than low degree nodes \cite{newman2002assortative}.
+Such a dissortative property hints a hub and spoke network structure, which is also reflected in the degree distribution, see Figure~\ref{fig:degreedist}.
 

### 2019-01-06 parseGraph.py

@@ -63,6 +63,7 @@ def basicStatistics(G):
     #print("LN's S-metric: ", smetric(G)) #0.6879664061934981
     print("LN average clustering coefficient", approximation.clustering_coefficient.average_clustering(G))
     print("LN's transitivity: ", nx.algorithms.cluster.transitivity(G))
+    print("Average shortest paths: ",nx.algorithms.shortest_paths.generic.average_shortest_path_length(G))
     #print("LN's largest clique size: ", nx.algorithms.approximation.clique.max_clique(G))
     #81 onion node :(
 

### 2019-01-07 article/main.tex
Added gitignore

@@
 
-\begin{wrapfigure}{r}{0.7\textwidth}
+\begin{wrapfigure}{r}{0.6\textwidth}
 	\begin{center}
@@
 \section{Lightning Network's Topology}
-\begin{wrapfigure}[18]{r}{5.5cm}
+\begin{wrapfigure}[20]{r}{5.5cm}
 	\begin{tabular}{ | l | c | }
@@
 		Number of payment channels & $16617$  \\ \hline
+		Average degree & $7.0891$ \\ \hline
 		Connected components & $2$  \\ \hline
@@
 		Radius & $3$ \\ \hline
+		Mean shortest path &  $2.80623$ \\ \hline
 		Transitivity& $0.1046$\\ \hline
@@
 
-LN gradually increased adoption and attraction throughout 2018, which resulted in 3 independent client implementations and \num[group-separator={,}]{2344} nodes joining LN as of 2019, January 3rd.
+LN gradually increased adoption and attraction throughout 2018, which resulted in 3 independent client implementations (c-lightning, eclair and lnd) and \num[group-separator={,}]{2344} nodes joining LN as of 2019, January 3rd.
 The density of a graph is defined as $D=\frac{2\mid E\mid}{\mid V\mid \mid V-1\mid}$  which is the ratio of present and potential edges.
@@
 
+Average shortest path length is $2.80623$, which signals that payments can easily be routed with a few hops throughout the whole network.
+Although this is far from being a straightforward task, since one also needs to take into consideration the capacity of individual payment channels along a candidate path.
+
 \section{Robustness of LN}
+It is a major question in network science how robust a given network is.
+LN, just like Bitcoin, is a permissionless network, where nodes can join and leave arbitrarily at any point in time.
+Nodes can also create new payment channels or close them any time.
+Furthermore as new payments are made, capacities of payment channels are changing steadily.
+Despite the dynamic nature of LN, its topology's characteristics remain constant after all.
+In this section we investigate how resilient is LN, whether it can effectively withhold random node failures or deliberate attacks.
 \subsection{Random Failures}
+\begin{wrapfigure}[15]{r}{5.5cm}
+	\begin{tabular}{ | l | c | }
+		\hline
+		Network & $f_c$  \\ \hline
+		Internet & $0.92$  \\ \hline
+		WWW & $0.88$ \\ \hline
+		US Power Grid & $0.61$  \\ \hline
+		Mobil Phone Call & $0.78$ \\ \hline
+		E-mail & $0.92$ \\ \hline
+		Science collaboration& $0.92$ \\ \hline
+		E. Coli Metabolism & $0.96$ \\ \hline
+		Yeast Protein Interactions & $0.88$ \\ \hline
+		LN & $0.00535$ \\ \hline
+	\end{tabular}
+	\caption{Random failures in networks. Values of critical thresholds for other real networks are taken from \cite{barabasi2016network}.}\label{fig:randfailures}
+\end{wrapfigure}
+
+Random failures are a realistic attack vector for LN.
+If nodes happen to be off-line due to bad connections or other reasons, they can not participate in routing payments anymore.
+Such a failure can be modeled as if a node and its edges are removed from the graph.
+We continually remove nodes from the graph, until the networks is broken into several isolated components.
+The fraction of nodes need to be removed from a network to break it into multiple connected components is called critical threshold and denoted as $f_c$.
+As Figure~\ref{fig:randfailures} displays LN is not capable of withstanding even random failures.
+This incapability is even more striking when compared to other real networks.
+
 \subsection{Targeted attacks}
+Targeted attacks on LN nodes are also a major concern as the short history of LN has already shown this.
+On 2018 March 21st \footnote{https://www.trustnodes.com/2018/03/21/lightning-network-ddos-sends-20-nodes}, $20\%$ of nodes were down due to a Distributed Denial of Service (DDoS) attack against LN nodes.
+Denial of Service (DoS) attacks are also quite probable by flooding HTLCs.
+These attack vectors are extremely harmful, especially if they are coordinated well.
+One might expect that not only state-sponsored attackers will have the resources to attack a small network like LN.
 \begin{figure}[h]
@@
 \section{Conclusion}
+false sense of security and robustness
 \section{Acknowledgements}

### 2019-01-07 parseGraph.py

@@ -20,7 +20,7 @@ allWeights = []
 
 def main():
     G=defineGraph(readFile())
-    basicStatistics(G)
+    #basicStatistics(G)
     #degreeDistribution(G) #percentile graph needs to be added
     #weightsDistribution(G)
     #shortestPaths(G)
@@ -30,7 +30,7 @@ def main():
     #randomVertexConnectivity(G)
     #centrality(G)
     #clusteringCoefficient(G)
-    #simpleStatistics(G)
+    simpleStatistics(G)
 
 #degreeCentrality
 
@@ -63,7 +63,7 @@ def basicStatistics(G):
     #print("LN's S-metric: ", smetric(G)) #0.6879664061934981
     print("LN average clustering coefficient", approximation.clustering_coefficient.average_clustering(G))
     print("LN's transitivity: ", nx.algorithms.cluster.transitivity(G))
-    print("Average shortest paths: ",nx.algorithms.shortest_paths.generic.average_shortest_path_length(G))
+    #print("Average shortest paths: ",nx.algorithms.shortest_paths.generic.average_shortest_path_length(G)) # 2.806222412074612
     #print("LN's largest clique size: ", nx.algorithms.approximation.clique.max_clique(G))
     #81 onion node :(
 

### 2019-01-07 article/main.tex
Privacy section is yet to come

@@
 Bitcoin's Lightning Network (LN) is a scalability solution for Bitcoin, which allows transactions to be issued with negligible fees and settle transactions instantly at scale.
-In order to use LN funds need to be locked in payment channels on the Bitcoin blockchain (Layer-1), that one may use them in LN (Layer-2).
+In order to use LN, funds need to be locked in payment channels on the Bitcoin blockchain (Layer-1), that one may use them in LN (Layer-2).
 LN is comprised of many payment channels forming a payment channel network.
-A few payment channels already enable anyone to efficiently, securely and privately route payments across the whole network.
-In this paper we argue that LN's current topological properties largely harms its value proposition and potential.
+LN promises that a few payment channels already enable anyone to efficiently, securely and privately route payments across the whole network.
+In this paper we quantify the structural properties of LN and argue that LN's current topological properties largely harms its value proposition and potential.
 \end{abstract}
@@
 \begin{wrapfigure}{r}{0.6\textwidth}
+	\captionsetup{justification=centering,margin=0.5cm}
 	\begin{center}
@@
 	\end{center}
-	\caption{LN's topology. Nodes with higher degree are highlighted with lighter colors}
+
+	\caption{LN's topology. Nodes with higher degree are highlighted with lighter colors and larger circles.}\label{fig:lntopology}
 	\vspace{-10pt}
@@
 \textbf{Our contributions.} We empirically measure and describe LN's topology and show that it is utterly centralized and fragile against both random failures and targeted attacks.
-These findings suggest that LN, unlike Bitcoin, is far from being reliable, censorship-resistant, decentralized and private.
+These findings suggest that LN, unlike Bitcoin, is undoubtedly far from being reliable, censorship-resistant, decentralized and private.
 \section{Lightning Network's Topology}
@@
 
+When a new node joins LN, it needs to select which other nodes it is trying to connect to.
+In every LN implementation one of the key goal of a node is to optimize its centrality by connecting to central nodes.
+This phenomena sets up a preferential attachment pattern.
+Betweenness centrality of a node $v$ is given by the expression $g(v)=\sum_{s\neq v \neq t}\frac{\sigma_{st}(v)}{\sigma_{st}},$ where $\sigma_{st}$ is the total number of shortest paths between node $s$ and $t$, whilst $\sigma_{st}(v)$ is the number of those paths, that pass through $v$.
+Closeness centrality  of a node $v$ is defined as $CC(u)=\frac{N}{\sum_{u\neq v}d(u,v)},$ where $N$ is the number nodes in the graph and $d(u,v)$ is the distance between node $u$ and $v$.
+Closeness centrality measures how close a node is to all other nodes.
+
+\begin{figure}[h]
+	\centering
+	\begin{minipage}{.6\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{betweennessCentrality.png}
+		\captionof{figure}{LN's betweenness centrality}
+		\label{fig:betweennescentrality}
+	\end{minipage}%
+	\begin{minipage}{.6\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{closenessCentrality.png}
+		\captionof{figure}{LN's closeness centrality}
+		\label{fig:closenesscentrality}
+	\end{minipage}
+\end{figure}
+
+Small-world architectures, like LN, exhibit high clustering with short path lenghts.
+The appropriate graph theoretic tool to asses clustering is the clustering coefficient \cite{watts1998collective}.
+Local clustering coefficient measures how well a node's neighbors are connected to each other, namely how close they are to being a clique.
+If a node $u$ has $deg(u)$ neighbors, then between these $deg(u)$ neighbors could be at maximum $\frac{1}{2}deg(u)(deg(u)-1)$ edges.
+If $N(u)$ denotes the set of $u$'s neighbors, then the local clustering coefficient is defined as $C(u)=\frac{2\mid (v,w): v,w \in N(u) \land (v,w) \in E \mid}{deg(u)(deg(u)-1)}$.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{clusteringCoefficient.png}
+	\caption{Local clustering coefficient of LN}\label{fig:localclustering}
+\end{figure}
+
+ LN's local clustering coefficient distribution suggestively captures that LN is essentially comprised of a small central clique and a loosely connected periphery.
+
 \section{Robustness of LN}
@@
 The fraction of nodes need to be removed from a network to break it into multiple connected components is called critical threshold and denoted as $f_c$.
-As Figure~\ref{fig:randfailures} displays LN is not capable of withstanding even random failures.
+As Figure~\ref{fig:randfailures}.
+displays LN is not capable of withstanding even random failures.
 This incapability is even more striking when compared to other real networks.
@@
 \subsection{Targeted attacks}
-Targeted attacks on LN nodes are also a major concern as the short history of LN has already shown this.
+Targeted attacks on LN nodes are also a major concern as the short history of LN has already shown it.
 On 2018 March 21st \footnote{https://www.trustnodes.com/2018/03/21/lightning-network-ddos-sends-20-nodes}, $20\%$ of nodes were down due to a Distributed Denial of Service (DDoS) attack against LN nodes.
@@
 One might expect that not only state-sponsored attackers will have the resources to attack a small network like LN.
+In the first attack scenario we removed 30 highest-degree nodes one by one starting with the most well-connected one and gradually witdhraw the subsequent high-degree nodes.
+We recorded the number of connected components.
+As it is shown in Figure~\ref{fig:vertexconnectivity}.
+even just removing the highest-degree node\footnote{http://rompert.com/} fragments the LN graph into 37 connected components!
+Altogether the removal of the $30$ largest hubs incurs LN to collapse into $424$ components.
 \begin{figure}[h]
 	\centering
-	\begin{minipage}{.5\textwidth}
+	\begin{minipage}{.6\textwidth}
 		\centering
 		\includegraphics[width=\linewidth]{vertexConnectivity.png}
-		\captionof{figure}{LN's vertex connectivity}
-		\label{fig:test1}
+		\captionof{figure}{LN's vertex connectivity, when all the $30$ largest hubs are removed one by one}
+		\label{fig:vertexconnectivity}
 	\end{minipage}%
-	\begin{minipage}{.5\textwidth}
+	\begin{minipage}{.6\textwidth}
 		\centering
-		\includegraphics[width=\linewidth]{edgeConnectivity.png}
-		\captionof{figure}{LN's edge connectivity}
-		\label{fig:test2}
+		\includegraphics[width=\linewidth]{vertexConnectivity1Removed.png}
+		\captionof{figure}{LN's vertex connectivity if only one high-degree node is removed from the graph.}
+		\label{fig:vertecconnectivity1removed}
 	\end{minipage}
@@
 
-\subsection{Fixing LN's resilience against attacks}
-percolation threshold
+We reasserted the targeted attack scenario, but for the second time we only removed one of the $30$ largest hubs and recorded the number of connected components.
+As it can be seen in Figure~\ref{fig:vertecconnectivity1removed} most of the hubs (25!) are so critical that their removal would be catastrophic for LN, namely they would leave behind several disconnected components.
+
+Such network fragmentations are unwanted in case of LN, because they would make payment routing substantially more challenging (one needs to split the payment over several routes) or even impossible (there would be no routes at all).
+An analogous dissolution would effectively render LN non-functional.
+
+\subsection{Fixing LN's resilience against random failures and attacks}
+Designing networks which are robust to random failures and targeted attacks appear to be a conflicting desire \cite{barabasi2016network}.
+For instance a star graph, the simplest hub and spoke network, is resilient to random failures.
+The removal of any set of spokes does not hurt the connectedness of the main component.
+However it can not withstand a targeted attack against its central node, since it would leave behind isolated spokes.
+
+Nonetheless, we could still enhance the network's attack tolerance by connecting its peripheral nodes \cite{barabasi2016network} and
+mandating newcomers to connect to not only hubs as current implementations do but also to at least a few random nodes.
+This would envolve that even the removal of major hubs would leave the connectedness of the major component intact.
 \section{Privacy}
@@
 \section{Conclusion}
-false sense of security and robustness
+Shiny figures of LN's topology, like Figure~\ref{fig:lntopology}, convey only false sense of security and robustness.
 \section{Acknowledgements}

### 2019-01-07 parseGraph.py

@@ -30,7 +30,7 @@ def main():
     #randomVertexConnectivity(G)
     #centrality(G)
     #clusteringCoefficient(G)
-    simpleStatistics(G)
+    #simpleStatistics(G)
 
 #degreeCentrality
 
@@ -147,13 +147,13 @@ def vertexConnectivity(G):
     print("what?",len(list(nx.connected_components(G))))
     for x in range(30):
         print(sortedNodes[x][0])
-        #G.remove_node(sortedNodes[x][0])
-        Gor[x].remove_node(sortedNodes[x][0])
+        G.remove_node(sortedNodes[x][0])
+        #Gor[x].remove_node(sortedNodes[x][0])
         comp.append(x+1)
-        #cnt.append(len(list(nx.connected_components(G))))
-        #print(x+1,len(list(nx.connected_components(G))))
-        cnt.append(len(list(nx.connected_components(Gor[x]))))
-        print(x+1,len(list(nx.connected_components(Gor[x]))))
+        cnt.append(len(list(nx.connected_components(G))))
+        print(x+1,len(list(nx.connected_components(G))))
+        #cnt.append(len(list(nx.connected_components(Gor[x]))))
+        #print(x+1,len(list(nx.connected_components(Gor[x]))))
         print(Gor[x].order())
 
     fig, ax = plt.subplots()

### 2019-01-11 article/main.tex
Approximating power-law exponent

@@
 LN is comprised of many payment channels forming a payment channel network.
-LN promises that a few payment channels already enable anyone to efficiently, securely and privately route payments across the whole network.
-In this paper we quantify the structural properties of LN and argue that LN's current topological properties largely harms its value proposition and potential.
+LN's promise is that a few payment channels already enable anyone to efficiently, securely and privately route payments across the whole network.
+In this paper we quantify the structural properties of LN and argue that LN's current topological properties could have been ameliorated in order to enable LN to reach its true potential.
 \end{abstract}
@@
 Without further advancements, the Bitcoin network can only settle $7$ transactions per second (tps), while mainstream centralized payment providers such as Visa and Mastercard can process approximately \num[group-separator={,}]{40000} tps in peak hours.
-Moreover one might need to pay large transaction fees on the Bitcoin network, while also need to wait 6 new blocks to be published in order to be certain enought that the transaction is included in the blockchain.
+Moreover one might need to pay large transaction fees on the Bitcoin network, while also need to wait 6 new blocks to be published in order to be certain enough that the transaction is included in the blockchain.
 
@@
 
-\textbf{Our contributions.} We empirically measure and describe LN's topology and show that it is utterly centralized and fragile against both random failures and targeted attacks.
-These findings suggest that LN, unlike Bitcoin, is undoubtedly far from being reliable, censorship-resistant, decentralized and private.
+\textbf{Our contributions.} We empirically measure and describe LN's topology and show how robust it is against both random failures and targeted attacks.
+These findings suggest that how LN's topology could be ameliorated in order to achieve its true potential.
 \section{Lightning Network's Topology}
@@
 Betweenness centrality of a node $v$ is given by the expression $g(v)=\sum_{s\neq v \neq t}\frac{\sigma_{st}(v)}{\sigma_{st}},$ where $\sigma_{st}$ is the total number of shortest paths between node $s$ and $t$, whilst $\sigma_{st}(v)$ is the number of those paths, that pass through $v$.
-Closeness centrality  of a node $v$ is defined as $CC(u)=\frac{N}{\sum_{u\neq v}d(u,v)},$ where $N$ is the number nodes in the graph and $d(u,v)$ is the distance between node $u$ and $v$.
+Closeness centrality  of a node $v$ is defined as $CC(u)=\frac{N}{\sum_{u\neq v}d(u,v)},$ where $N$ is the number of nodes in the graph and $d(u,v)$ is the distance between node $u$ and $v$.
 Closeness centrality measures how close a node is to all other nodes.
@@
 		Mobil Phone Call & $0.78$ \\ \hline
-		E-mail & $0.92$ \\ \hline
 		Science collaboration& $0.92$ \\ \hline
@@
 		Yeast Protein Interactions & $0.88$ \\ \hline
-		LN & $0.00535$ \\ \hline
+		LN & $0.60$ \\ \hline
 	\end{tabular}
@@
 As Figure~\ref{fig:randfailures}.
-displays LN is not capable of withstanding even random failures.
-This incapability is even more striking when compared to other real networks.
+displays LN is fairly capable of withstanding random failures, however not as well as other real world networks.
 
@@
 We reasserted the targeted attack scenario, but for the second time we only removed one of the $30$ largest hubs and recorded the number of connected components.
-As it can be seen in Figure~\ref{fig:vertecconnectivity1removed} most of the hubs (25!) are so critical that their removal would be catastrophic for LN, namely they would leave behind several disconnected components.
+As it can be seen in Figure~\ref{fig:vertecconnectivity1removed} most of the hubs, 25, would leave behind several disconnected components.
+
+\begin{wrapfigure}[15]{r}{5.5cm}
+	\begin{tabular}{ | l | c | }
+		\hline
+		Network & $f_c$  \\ \hline
+		Internet & $0.16$  \\ \hline
+		WWW & $0.12$ \\ \hline
+		US Power Grid & $0.20$  \\ \hline
+		Mobil Phone Call & $0.20$ \\ \hline
+		Science collaboration& $0.27$ \\ \hline
+		E. Coli Metabolism & $0.49$ \\ \hline
+		Yeast Protein Interactions & $0.16$ \\ \hline
+		LN & $0.07$ \\ \hline
+	\end{tabular}
+	\caption{Real networks under targeted attacks. Values of critical thresholds for other real networks are taken from \cite{barabasi2016network}.}\label{fig:randfailures}
+\end{wrapfigure}
 
 Such network fragmentations are unwanted in case of LN, because they would make payment routing substantially more challenging (one needs to split the payment over several routes) or even impossible (there would be no routes at all).
-An analogous dissolution would effectively render LN non-functional.
 
-\subsection{Fixing LN's resilience against random failures and attacks}
+\subsection{Improving LN's resilience against random failures and attacks}
 Designing networks which are robust to random failures and targeted attacks appear to be a conflicting desire \cite{barabasi2016network}.

### 2019-01-11 parseGraph.py

@@ -8,9 +8,12 @@ import matplotlib.ticker as mticker
 from matplotlib.ticker import MaxNLocator
 import collections
 import numpy as np
+from mpmath import mp
+from decimal import *
 import string
 from random import randint
 from random import seed
+from scipy import special as spcl
 import heapq
 from networkx.algorithms import approximation
 
@@ -31,11 +34,73 @@ def main():
     #centrality(G)
     #clusteringCoefficient(G)
     #simpleStatistics(G)
+    fittingGamma(G)
+
+def gammaF(G, Kmin):
+    sum = 0
+    counter = 0
+    for x in G.nodes():
+        if(G.degree(x)>=Kmin):
+            sum += np.log(G.degree(x) / (Kmin - 0.5))
+            counter+=1
+    gamma = 1 + counter * (1 / sum)
+    return gamma
 
 #degreeCentrality
+def fittingGamma(G):
+    degree_sequence = sorted([d for n, d in G.degree()], reverse=True)  # degree sequence
+    # print "Degree sequence", degree_sequence
+    degreeCount = collections.Counter(degree_sequence)
+    deg, cnt = zip(*degreeCount.items())
+
+    minmaxD = 100
+    optimalK = 0
+    maxD = []
+    for Kmin in deg:
+        gamma = gammaF(G,Kmin)
+
+        maxDistance = 0
+        cdf = [] #cumulative distribution func
+        cdfOrdered = {}
+
+        for y in deg:
+            if(spcl.zeta(gamma,Kmin)!=0.0):
+                CDF = 1-(spcl.zeta(gamma,y))/(spcl.zeta(gamma,Kmin))
+            else:
+                CDF = 0
+            cdf.append(CDF)
+            cdfOrdered[y] = CDF
+
+        #Kolmogorov-Smirnov test
+        for z in deg:
+            if (z >= Kmin):
+                if abs(cdfOrdered[z]-(empiricalCDF(deg,cnt,z)/G.order()))>maxDistance:
+                    maxDistance = abs(cdfOrdered[z]-(z/G.order()))
+        if maxDistance < minmaxD:
+            minmaxD = maxDistance
+            optimalK = Kmin
+        maxD.append(maxDistance)
+
+    deviation=1/math.sqrt(G.order()*((mp.zeta(gamma,optimalK,2)/spcl.zeta(gamma,optimalK))-math.pow((mp.zeta(gamma,optimalK,1)/spcl.zeta(gamma,optimalK)),2)))
+
+    print(optimalK)
[…]

### 2019-01-12 article/main.tex
Fitting gamma ready, Percolation started

@@
 \author[1]{István András Seres}
+\author[1]{László Gulyás}
 \author[1]{Dániel A. Nagy}
@@
 \section{Lightning Network's Topology}
-\begin{wrapfigure}[20]{r}{5.5cm}
+\begin{wrapfigure}[22]{r}{5.5cm}
 	\begin{tabular}{ | l | c | }
@@
 The low transitivity, fraction of present and possible triangles in the graph, highlights the sparseness of LN as well.
-
-However LN also exhibits somewhat scale-free properties as the s-metric suggests.
-S-metric was first introduced by Lun Li et al.
-in \cite{li2005towards} and defined as $s(G)=\sum_{(u,v)\in E}deg(u)deg(v)$.
-The closer to $1$  s-metric of $G$ is, the more scale-free the network.
-Diameter and radius of LN suggests that LN is a small world.
-Somewhat scale-freeness is also exhibited in the degree distribution of LN.
-Majority of nodes have very few payment channels, although there are a few hubs who have significantly more connections as it can be seen in Figure~\ref{fig:degreedist}.
 
@@
  LN's local clustering coefficient distribution suggestively captures that LN is essentially comprised of a small central clique and a loosely connected periphery.
+
+\subsection{Scale-freeness of LN}
+
+LN might exhibit scale-free properties as the s-metric suggests.
+S-metric was first introduced by Lun Li et al.
+in \cite{li2005towards} and defined as $s(G)=\sum_{(u,v)\in E}deg(u)deg(v)$.
+The closer to $1$  s-metric of $G$ is, the more scale-free the network.
+Diameter and radius of LN suggests that LN is a small world.
+Somewhat scale-freeness is also exhibited in the degree distribution of LN.
+Majority of nodes have very few payment channels, although there are a few hubs who have significantly more connections as it can be seen in Figure~\ref{fig:degreedist}.
+
+The scale-freeness of LN is further justified also by applying the method introduced in \cite{clauset2009power}.
+The maximum-likelihood fitting asserted that the best fit for the empirical degree distribution is a power law function with exponent $\gamma=-2.1387$.
+The goodness-of-fit of the scale-free model was ascertained by the Kolmogorov-Smirnov statistic.
+We found that the $p$-value of the scale-free hypothesis is $p=0.8172$, which is accurate within $0.01$.
+Therefore the scale-free hypothesis is plausible for the empirical degree distribution of LN.
 
@@
 \section{Conclusion}
+In summary, a better understanding of the network topology is essential
+to improve the robustness of complex systems. We can enhance robustness
+by either designing network topologies that are simultaneously
+robust to both random failures and attacks, or by interventions that limit
+the spread of cascading failures.
+resilience depends on topology
 Shiny figures of LN's topology, like Figure~\ref{fig:lntopology}, convey only false sense of security and robustness.
 \section{Acknowledgements}
+We are grateful for the insightful comments and discussions to Chris Buckland, Olaoluwa Osuntokun and Alex Bosworth.
 

### 2019-01-12 parseGraph.py

@@ -5,6 +5,8 @@ import math
 import matplotlib.pyplot as plt
 import matplotlib.colors as mcolors
 import matplotlib.ticker as mticker
+import random
+import operator
 from matplotlib.ticker import MaxNLocator
 import collections
 import numpy as np
@@ -23,6 +25,11 @@ allWeights = []
 
 def main():
     G=defineGraph(readFile())
+    degree_sequence = sorted([d for n, d in G.degree()], reverse=True)  # degree sequence
+    # print "Degree sequence", degree_sequence
+    degreeCount = collections.Counter(degree_sequence)
+    deg, cnt = zip(*degreeCount.items())
+
     #basicStatistics(G)
     #degreeDistribution(G) #percentile graph needs to be added
     #weightsDistribution(G)
@@ -34,35 +41,154 @@ def main():
     #centrality(G)
     #clusteringCoefficient(G)
     #simpleStatistics(G)
-    fittingGamma(G)
+    #fittingGamma(deg, cnt)
+    #goodnessOfFit(deg, cnt)
+    #percolationThresholdPrediction(deg)
+    attackingBetweenness(G,deg, cnt)
+    #attackingHighDegrees(G, deg, cnt)
 
-def gammaF(G, Kmin):
+#Percolation Threshold: 565
+def attackingHighDegrees(G, deg, cnt):
+    highestDegrees = sorted(G.degree, key=lambda x: x[1], reverse=True)
+    print(highestDegrees)
+
+    originalGiantComponentSize = len(list(nx.connected_components(G))[0])
+    percolationThreshold = 0
+    for nodes in highestDegrees:
+        G.remove_node(nodes[0])
+        percolationThreshold+=1
+        print(percolationThreshold,len(list(nx.connected_components(G))[0]))
+        tooLarge = False
+        for x in range(len(list(nx.connected_components(G)))):
+            if tooLarge: break
+            if (len(list(nx.connected_components(G))[x]) > originalGiantComponentSize / 100):
+                tooLarge = True
+
+        if tooLarge==False:
+            print("Percolation Threshold: ", percolationThreshold)
+            break
+
+#Percolation Threshold:  561 (betweenness centrality)
+#Percolation Threshold: 1171 (closeness centrality)
+def attackingBetweenness(G, deg, cnt):
[…]

### 2019-01-15 article/main.tex
Attack effect on avg shortest paths

@@
 When a new node joins LN, it needs to select which other nodes it is trying to connect to.
-In every LN implementation one of the key goal of a node is to optimize its centrality by connecting to central nodes.
+In the \textit{lnd} LN implementation one of the key goal of a node is to optimize its centrality by connecting to central nodes.
 This phenomena sets up a preferential attachment pattern.
+Other LN implementations rely on their users to create channels manually, which also most probably end up users connecting to high-degree nodes.
 Betweenness centrality of a node $v$ is given by the expression $g(v)=\sum_{s\neq v \neq t}\frac{\sigma_{st}(v)}{\sigma_{st}},$ where $\sigma_{st}$ is the total number of shortest paths between node $s$ and $t$, whilst $\sigma_{st}(v)$ is the number of those paths, that pass through $v$.
@@
 In this section we investigate how resilient is LN, whether it can effectively withhold random node failures or deliberate attacks.
+
+Measuring robustness means that one gradually removes nodes and/or edges from the graph, until the giant component is broken into several isolated components.
+The fraction of nodes need to be removed from a network to break it into multiple isolated connected components is called the percolation threshold and denoted as $f_c$.
+In real networks percolation threshold can be well estimated by the point where the giant component first drops below $1\%$ of its original size \cite{barabasi2016network}.
 \subsection{Random Failures}
-\begin{wrapfigure}[15]{r}{5.5cm}
+\begin{wrapfigure}[16]{r}{5.5cm}
 	\begin{tabular}{ | l | c | }
@@
 		Yeast Protein Interactions & $0.88$ \\ \hline
-		LN & $0.60$ \\ \hline
+		LN & $0.96$ \\ \hline
 	\end{tabular}
@@
 Such a failure can be modeled as if a node and its edges are removed from the graph.
-We continually remove nodes from the graph, until the networks is broken into several isolated components.
-The fraction of nodes need to be removed from a network to break it into multiple connected components is called critical threshold and denoted as $f_c$.
-As Figure~\ref{fig:randfailures}.
-displays LN is fairly capable of withstanding random failures, however not as well as other real world networks.
 
+For scale-free networks with degree distribution $P_{k}=k^{-\gamma}$, where $2 < \gamma < 3$ the percolation threshold can be calculated by applying the Molloy-Reed criteria, ie.
+$f_{c}=1-\frac{1}{\frac{\gamma-2}{3-\gamma}k_{min}^{\gamma-2}k_{max}^{3-\gamma}-1}$, where $k_{min}$ and $k_{max}$ denote the lowest and highest degree nodes respectively.
+This formula yields $f_c=0.9797$ for LN in case of random failures.
+This value is indeed close to the percolation threshold measured by network simulation as shown in Figure~\ref{fig:randfailures}, that is, LN provides an evidence of topological stability under random failures.
+
+\newpage
 \subsection{Targeted attacks}
@@
 One might expect that not only state-sponsored attackers will have the resources to attack a small network like LN.
-In the first attack scenario we removed 30 highest-degree nodes one by one starting with the most well-connected one and gradually witdhraw the subsequent high-degree nodes.
+In the first attack scenario we removed 30 highest-degree nodes one by one starting with the most well-connected one and gradually withdraw the subsequent high-degree nodes.
 We recorded the number of connected components.
@@
 even just removing the highest-degree node\footnote{http://rompert.com/} fragments the LN graph into 37 connected components!
-Altogether the removal of the $30$ largest hubs incurs LN to collapse into $424$ components.
+Altogether the removal of the $30$ largest hubs incurs LN to collapse into $424$ components, although most of these are isolated vertices.
+This symptom can be explained by the experienced dissortativity, namely hubs tend to be at the periphery.
 \begin{figure}[h]
@@
 
-\begin{wrapfigure}[15]{r}{5.5cm}
+\begin{wrapfigure}[21]{r}{5.5cm}
+	\caption{Real networks under targeted attacks. Values of critical thresholds for other real networks are taken from \cite{barabasi2016network} and \cite{lin2017assessing}.}\label{fig:randfailures}
 	\begin{tabular}{ | l | c | }
@@
 		WWW & $0.12$ \\ \hline
+		Facebook & $0.28$ \\ \hline
+		Euroroad & $0.59$ \\ \hline
 		US Power Grid & $0.20$  \\ \hline
@@
 		Yeast Protein Interactions & $0.16$ \\ \hline
-		LN & $0.07$ \\ \hline
+		LN & $0.14$ \\ \hline
 	\end{tabular}
-	\caption{Real networks under targeted attacks. Values of critical thresholds for other real networks are taken from \cite{barabasi2016network}.}\label{fig:randfailures}
 \end{wrapfigure}
@@
 Such network fragmentations are unwanted in case of LN, because they would make payment routing substantially more challenging (one needs to split the payment over several routes) or even impossible (there would be no routes at all).
+
+Furthermore we estimated the percolation threshold by simulating two attacking strategies.
+In the first scenario we removed high degree nodes one by one (high degree removal attack, HDR) and in the second we removed nodes with the highest betweenness centrality (high betweenness removal attack, HBR).
+Note that in both cases after each node removal we recalculated which node has the highest degree or betweenness centrality in order to have a more powerful attack.
+We found out that $f_{c}=0.1627$ for removing high degree nodes, while for removing high betweenness centrality nodes $f_{c}=0.1409$, therefore choosing to remove high betweenness centrality nodes is a better strategy as it can also be seen in Figure~\ref{fig:randhighbetween}.
+
+\begin{wrapfigure}{r}{0.7\textwidth}
+	\captionsetup{justification=centering,margin=0.1cm}
+	\caption{High degree removal (HDR) attack effects average shortest path lengths}\label{fig:attackeffectpath}
+	\begin{center}
+		\includegraphics[width=\linewidth]{attackEffectPathLength.png}	
+	\end{center}
+\end{wrapfigure}
+
+Node outage not only affects robustness and connectivity properties, but also affects average shortest path lengths.
+Although the outage of random nodes does not significantly increase the average shortest path lengths in LN, targeted attacks against hubs increase distances between remaining nodes.
+The spillage of high-degree nodes not only decrease the amount of available liquidity but also rapidly increase the necessary hops along payment routes as Figure~\ref{fig:attackeffectpath} suggests.
+This could cause increased ratio of failed payments due to larger payment routes.
+
+\begin{figure}{r}
+	\captionsetup{justification=centering,margin=0.5cm}
+	\begin{center}
+		\includegraphics[width=\linewidth]{randomHighBetweenness.png}	
+	\end{center}	
+	\caption{Percolation thresholds for various attack scenarios: $f_{c}^{HDR}=0.1627$, $f_{c}^{HBR}=0.1409$, $f_{c}^{RND}=0.9645$}\label{fig:randhighbetween}
+	\vspace{-10pt}
+\end{figure}
 
@@
 Nonetheless, we could still enhance the network's attack tolerance by connecting its peripheral nodes \cite{barabasi2016network} and
-mandating newcomers to connect to not only hubs as current implementations do but also to at least a few random nodes.
-This would envolve that even the removal of major hubs would leave the connectedness of the major component intact.
-\section{Privacy}
-topological anomalies have privacy implications, low usage of tor, even tor can not help
+mandating newcomers to connect to not only hubs as current implementations do but also to at least a few random nodes. This would largely increase robustness of LN even against targeted attacks.
+
 \section{Conclusion}
 In summary, a better understanding of the network topology is essential
-to improve the robustness of complex systems. We can enhance robustness
-by either designing network topologies that are simultaneously
-robust to both random failures and attacks, or by interventions that limit
-the spread of cascading failures.
-resilience depends on topology
-Shiny figures of LN's topology, like Figure~\ref{fig:lntopology}, convey only false sense of security and robustness.
+to improve the robustness of complex systems, like LN.
+Network resilience depends on topology.
+LN is well approximated by the scale-free model and also its attack tolerance properties are similar to that of scale-free networks; namely, LN is robust against random failures, however it is quite vulnerable against targeted attacks.
+Shiny figures of LN's topology, like Figure~\ref{fig:lntopology}, convey only false sense of security and robustness, therefore to provide robust Layer 2 solutions for blockchains, the community needs to aim at building resilient network topologies.
 \section{Acknowledgements}

### 2019-01-15 parseGraph.py

@@ -30,7 +30,7 @@ def main():
     degreeCount = collections.Counter(degree_sequence)
     deg, cnt = zip(*degreeCount.items())
 
-    #basicStatistics(G)
+    basicStatistics(G)
     #degreeDistribution(G) #percentile graph needs to be added
     #weightsDistribution(G)
     #shortestPaths(G)
@@ -44,68 +44,105 @@ def main():
     #fittingGamma(deg, cnt)
     #goodnessOfFit(deg, cnt)
     #percolationThresholdPrediction(deg)
-    attackingBetweenness(G,deg, cnt)
-    #attackingHighDegrees(G, deg, cnt)
+    #attackingBetweenness(G,deg, cnt)
+    #attackingHighDegrees(G)
+    #drawHistogram(G)
 
-#Percolation Threshold: 565
-def attackingHighDegrees(G, deg, cnt):
-    highestDegrees = sorted(G.degree, key=lambda x: x[1], reverse=True)
-    print(highestDegrees)
-
+def drawHistogram(G): #attack effect on avg shortest path length
     originalGiantComponentSize = len(list(nx.connected_components(G))[0])
-    percolationThreshold = 0
-    for nodes in highestDegrees:
-        G.remove_node(nodes[0])
-        percolationThreshold+=1
-        print(percolationThreshold,len(list(nx.connected_components(G))[0]))
-        tooLarge = False
-        for x in range(len(list(nx.connected_components(G)))):
-            if tooLarge: break
-            if (len(list(nx.connected_components(G))[x]) > originalGiantComponentSize / 100):
-                tooLarge = True
+    a=[2.806222412074612, 2.871217085442275, 2.91560045459128, 2.9437603442568685, 2.9740025229103972, 3.0045886322304565, 3.037044687225701, 3.0553851019952716, 3.075570909398242, 3.0890175949054375, 3.1157498785629887, 3.131813039281431, 3.146865049134942, 3.163353070623199, 3.1801390239729423, 3.1856303960443033, 3.2041163947454585, 3.2125176424347455, 3.226031083245262, 3.2354480642086663, 3.2458709321869597, 3.2528784561124127, 3.2657448307356463, 3.275644221485353, 3.2882485866327467, 3.3025002028102657, 3.3139604454666687, 3.325104794319505, 3.3376269239216745, 3.3465795761157207, 3.354999742940903]
+    b = list(range(0, 31))
[…]

### 2019-01-15 article/main.tex
Fixing abstract and conclusion by Dani

@@
 \begin{abstract}
-Bitcoin's Lightning Network (LN) is a scalability solution for Bitcoin, which allows transactions to be issued with negligible fees and settle transactions instantly at scale.
-In order to use LN, funds need to be locked in payment channels on the Bitcoin blockchain (Layer-1), that one may use them in LN (Layer-2).
+Bitcoin's Lightning Network (LN) is a scalability solution for Bitcoin allowing transactions to be issued with negligible fees and settled instantly at scale.
+In order to use LN, funds need to be locked in payment channels on the Bitcoin blockchain (Layer-1) for subsequent use in LN (Layer-2).
 LN is comprised of many payment channels forming a payment channel network.
-LN's promise is that a few payment channels already enable anyone to efficiently, securely and privately route payments across the whole network.
-In this paper we quantify the structural properties of LN and argue that LN's current topological properties could have been ameliorated in order to enable LN to reach its true potential.
+LN's promise is that relatively few payment channels already enable anyone to efficiently, securely and privately route payments across the whole network.
+In this paper, we quantify the structural properties of LN and argue that LN's current topological properties can be ameliorated in order to improve the security of LN, enabling it to reach its true potential.
 \end{abstract}
-\keywords{Bitcoin, Lightning Network, Network Topology, Payment Channel Network}
+\keywords{Bitcoin, Lightning Network, Network Security, Network Topology, Payment Channel Network, Network Robustness}
 
@@
 
-LN gradually increased adoption and attraction throughout 2018, which resulted in 3 independent client implementations (c-lightning, eclair and lnd) and \num[group-separator={,}]{2344} nodes joining LN as of 2019, January 3rd.
+LN gradually increased adoption and attraction throughout 2018, which resulted in 3 independent client implementations (c-lightning\footnote{https://github.com/ElementsProject/lightning/}, eclair\footnote{https://github.com/ACINQ/eclair} and lnd\footnote{https://github.com/lightningnetwork/lnd}) and \num[group-separator={,}]{2344} nodes joining LN as of 2019, January 3rd.
 The density of a graph is defined as $D=\frac{2\mid E\mid}{\mid V\mid \mid V-1\mid}$  which is the ratio of present and potential edges.
@@
 	\begin{center}
-		\includegraphics[width=0.85\textwidth]{degreehistogramlogscale.png}
+		\includegraphics[width=0.85\textwidth]{degreehistogramloglogscale.png}
 	\end{center}	
@@
 
-\subsection{Scale-freeness of LN}
+\subsection{Analysis of LN's degree distribution}
 
@@
 In summary, a better understanding of the network topology is essential
-to improve the robustness of complex systems, like LN.
-Network resilience depends on topology.
-LN is well approximated by the scale-free model and also its attack tolerance properties are similar to that of scale-free networks; namely, LN is robust against random failures, however it is quite vulnerable against targeted attacks.
-Shiny figures of LN's topology, like Figure~\ref{fig:lntopology}, convey only false sense of security and robustness, therefore to provide robust Layer 2 solutions for blockchains, the community needs to aim at building resilient network topologies.
+for improving the robustness of complex systems, like LN.
+Networks' resilience depends on their topology.
+LN is well approximated by the scale-free model and also its attack tolerance properties are similar to those of scale-free networks; in particular, while LN is robust against random failures, it is quite vulnerable in the face of targeted attacks.
+High-level depictions of LN's topology, like Figure~\ref{fig:lntopology}, convey a false image of security and robustness.
+As we have demonstrated, LN is structurally weak against rational adversaries.
+Thus, to provide robust Layer 2 solutions for blockchains, such as LN and Raiden, the community needs to aim at building resilient network topologies.
 \section{Acknowledgements}

### 2019-01-15 parseGraph.py

@@ -47,6 +47,25 @@ def main():
     #attackingBetweenness(G,deg, cnt)
     #attackingHighDegrees(G)
     #drawHistogram(G)
+    improvingRobustness(G)
+
+def improvingRobustness(G):
+    originalGiantComponentSize = len(list(nx.connected_components(G))[0])
+    originalRobustness = 0
+    #G.remove_nodes_from(list(nx.connected_components(G))[1])
+    percolationThreshold = 0
+    for x in range(1000):
+        highestDegrees = sorted(G.degree, key=lambda x: x[1], reverse=True)
+        G.remove_node(next(iter(highestDegrees))[0])
+        percolationThreshold += 1
+        largest_cc = max(nx.connected_components(G), key=len)
+        originalRobustness+=(len(largest_cc)/(originalGiantComponentSize*originalGiantComponentSize))
+        print(x, originalRobustness)
+        if (len(largest_cc) < originalGiantComponentSize / 100):
+            print("Percolation Threshold: ", percolationThreshold, percolationThreshold / originalGiantComponentSize)
+            break
+
+
 
 def drawHistogram(G): #attack effect on avg shortest path length
     originalGiantComponentSize = len(list(nx.connected_components(G))[0])
@@ -291,7 +310,7 @@ def basicStatistics(G):
     #print("LN rich-club coefficient: ", nx.algorithms.richclub.rich_club_coefficient(G))
     #print("LN rich-club normalized coefficient: ", nx.algorithms.richclub.rich_club_coefficient(G, normalized=True))
     #print(list(nx.connected_components(G))[1])
-    G.remove_nodes_from(list(nx.connected_components(G))[1]) #there is a small second component
+    #G.remove_nodes_from(list(nx.connected_components(G))[1]) #there is a small second component
     #print("LN diameter: ", nx.algorithms.distance_measures.diameter(G)) #6
     #print("LN radius", nx.algorithms.distance_measures.radius(G)) #3
     #print("LN Wiener index", nx.algorithms.wiener_index(G)) #7686159.0
@@ -303,6 +322,7 @@ def basicStatistics(G):
     print("LN's transitivity: ", nx.algorithms.cluster.transitivity(G))
     #print("Average shortest paths: ",nx.algorithms.shortest_paths.generic.average_shortest_path_length(G)) # 2.806222412074612
     #print("LN's largest clique size: ", nx.algorithms.approximation.clique.max_clique(G))
[…]

### 2019-01-15 article/main.tex
Fixing LNs topology

@@
 
-\textbf{Our contributions.} We empirically measure and describe LN's topology and show how robust it is against both random failures and targeted attacks.
-These findings suggest that how LN's topology could be ameliorated in order to achieve its true potential.
+\textbf{Our contributions.} We empirically measure\footnote{https://github.com/seresistvanandras/LNTopology} and describe LN's topology and show how robust it is against both random failures and targeted attacks.
+These findings suggest that LN's topology can be ameliorated in order to achieve its true potential.
 \section{Lightning Network's Topology}
-\begin{wrapfigure}[22]{r}{5.5cm}
+\begin{wrapfigure}[20]{r}{5.5cm}
 	\begin{tabular}{ | l | c | }
@@
 In the following we are going to analyze this dataset.
+Although the number of nodes and payment channels are permanently changing in LN, we observed through several snapshots that the main topological characteristics (density, average degree, transitivity, nature of degree distribution) remained unchanged.
+We leave it for future work to analyze the dynamic properties of LN.
 
@@
 However it can not withstand a targeted attack against its central node, since it would leave behind isolated spokes.
+Furthermore when one attempts increasing robustness of a network, they do desire not to decrease the connectivity of nodes.
 
-Nonetheless, we could still enhance the network's attack tolerance by connecting its peripheral nodes \cite{barabasi2016network} and
-mandating newcomers to connect to not only hubs as current implementations do but also to at least a few random nodes. This would largely increase robustness of LN even against targeted attacks.
+A similar optimization strategy of robustness and connectivity \cite{shargel2003optimization} could be applied to LN as well.
+We leave it for future work to empirically assess the robustness and connectivity gains if strategy of \cite{shargel2003optimization} would be implemented in LN client implementations.
+
+Nonetheless, we can still enhance the network's attack tolerance by connecting its peripheral nodes \cite{barabasi2016network}.
+This could be achieved by LN client implementations by implicitly mandating newcomers to connect to not only hubs, as current implementations do, but also to at least a few random nodes.
+This would largely increase robustness of LN even against targeted attacks.
 

### 2019-01-15 parseGraph.py

@@ -310,7 +310,7 @@ def basicStatistics(G):
     #print("LN rich-club coefficient: ", nx.algorithms.richclub.rich_club_coefficient(G))
     #print("LN rich-club normalized coefficient: ", nx.algorithms.richclub.rich_club_coefficient(G, normalized=True))
     #print(list(nx.connected_components(G))[1])
-    #G.remove_nodes_from(list(nx.connected_components(G))[1]) #there is a small second component
+    G.remove_nodes_from(list(nx.connected_components(G))[1]) #there is a small second component
     #print("LN diameter: ", nx.algorithms.distance_measures.diameter(G)) #6
     #print("LN radius", nx.algorithms.distance_measures.radius(G)) #3
     #print("LN Wiener index", nx.algorithms.wiener_index(G)) #7686159.0
@@ -574,7 +574,7 @@ def defineGraph(data) -> object:
 
 ##https://graph.lndexplorer.com/api/graph
 def readFile() -> object:
-    with open('graph20190115.json') as f:
+    with open('graph.json') as f:
         data = json.load(f)
     return data['edges']
 

### 2019-01-16 article/main.tex
Clearing literature from github

@@
 
-A similar optimization strategy of robustness and connectivity \cite{shargel2003optimization} could be applied to LN as well.
+A similar optimization strategy of robustness and connectivity to that of \cite{shargel2003optimization} could be applied to LN as well.
 We leave it for future work to empirically assess the robustness and connectivity gains if strategy of \cite{shargel2003optimization} would be implemented in LN client implementations.
@@
 As we have demonstrated, LN is structurally weak against rational adversaries.
-Thus, to provide robust Layer 2 solutions for blockchains, such as LN and Raiden, the community needs to aim at building resilient network topologies.
+Thus, to provide robust Layer-2 solutions for blockchains, such as LN and Raiden, the community needs to aim at building resilient network topologies.
 \section{Acknowledgements}

### 2019-01-17 article/main.tex
Fixes thanks to Daniel Goldman

@@
 
-To alleviate these scalability issues the Lightning Network (LN) is designed in 2016 \cite{poon2016bitcoin}, and launched in 2018, January.
-The main insight of LN is that transactions can be issued also off-blockchain in a trust-minimized manner achieving instant transaction confirmation times with negligible fees, whilst retaining the security of the underlying blockchain.
+To alleviate these scalability issues the Lightning Network (LN) was designed in 2016 \cite{poon2016bitcoin}, and launched in 2018, January.
+The main insight of LN is that transactions can be issued off-blockchain in a trust-minimized manner achieving instant transaction confirmation times with negligible fees, whilst retaining the security of the underlying blockchain.
 
@@
 As it is shown in Figure \ref{fig:properties}.
-LN is quite a parse graph.
+LN is quite a sparse graph.
 This is further justified by the fact that LN has \num[group-separator={,}]{530} bridges, edges which deletion increases the number of connected components.
-Although LN is consisted of $2$ components, the second component has only $3$ nodes.
+Although LN consists of $2$ components, the second component has only $3$ nodes.
 The low transitivity, fraction of present and possible triangles in the graph, highlights the sparseness of LN as well.
@@
 
-Average shortest path length is $2.80623$, which signals that payments can easily be routed with a few hops throughout the whole network.
+Average shortest path length is $2.80623$, without taking into account capacities of edges, which signals that payments can easily be routed with a few hops throughout the whole network.
 Although this is far from being a straightforward task, since one also needs to take into consideration the capacity of individual payment channels along a candidate path.
@@
 When a new node joins LN, it needs to select which other nodes it is trying to connect to.
-In the \textit{lnd} LN implementation one of the key goal of a node is to optimize its centrality by connecting to central nodes.
+In the \textit{lnd} LN implementation key goals for a node is to optimize its centrality by connecting to central nodes.
 This phenomena sets up a preferential attachment pattern.
-Other LN implementations rely on their users to create channels manually, which also most probably end up users connecting to high-degree nodes.
+Other LN implementations rely on their users to create channels manually, which also most likely leads to users connecting to high-degree nodes.
 Betweenness centrality of a node $v$ is given by the expression $g(v)=\sum_{s\neq v \neq t}\frac{\sigma_{st}(v)}{\sigma_{st}},$ where $\sigma_{st}$ is the total number of shortest paths between node $s$ and $t$, whilst $\sigma_{st}(v)$ is the number of those paths, that pass through $v$.
@@
 Despite the dynamic nature of LN, its topology's characteristics remain constant after all.
-In this section we investigate how resilient is LN, whether it can effectively withhold random node failures or deliberate attacks.
+In this section we investigate how resilient LN is, whether it can effectively withhold random node failures or deliberate attacks.
 
 Measuring robustness means that one gradually removes nodes and/or edges from the graph, until the giant component is broken into several isolated components.
-The fraction of nodes need to be removed from a network to break it into multiple isolated connected components is called the percolation threshold and denoted as $f_c$.
+The fraction of nodes that need to be removed from a network to break it into multiple isolated connected components is called the percolation threshold and is denoted as $f_c$.
 In real networks percolation threshold can be well estimated by the point where the giant component first drops below $1\%$ of its original size \cite{barabasi2016network}.
@@
 This value is indeed close to the percolation threshold measured by network simulation as shown in Figure~\ref{fig:randfailures}, that is, LN provides an evidence of topological stability under random failures.
+In particular this is due to the fact that in LN a randomly selected node is unlikely to affect the network as a whole, since an average node is not significantly contributing to the network's topological connectivity, see also degree distribution at Figure~\ref{fig:degreedist}.
 
@@
 \section{Acknowledgements}
-We are grateful for the insightful comments and discussions to Chris Buckland, Olaoluwa Osuntokun and Alex Bosworth.
+We are grateful for the insightful comments and discussions to Chris Buckland, Daniel Goldman, Olaoluwa Osuntokun and Alex Bosworth.
 

### 2019-01-17 parseGraph.py

@@ -574,7 +574,7 @@ def defineGraph(data) -> object:
 
 ##https://graph.lndexplorer.com/api/graph
 def readFile() -> object:
-    with open('graph.json') as f:
+    with open('graph.json')ll e as f:
         data = json.load(f)
     return data['edges']
 

### 2019-02-19 article/Springer/LNTopology.tex
Added Springer version of the paper

--- 2019-01-17 article/main.tex
@@
-\documentclass[a4paper]{article}
-
-%% Language and font encodings
+% This is samplepaper.tex, a sample chapter demonstrating the
+% LLNCS macro package for Springer Computer Science proceedings;
+% Version 2.20 of 2017/10/04
+%
+\documentclass[runningheads]{llncs}
+%
+\usepackage{graphicx}
+% Used for displaying a sample figure. If possible, figure files should
+% be included in EPS format.
+%
+% If you use the hyperref package, please uncomment the following line
+% to display URLs in blue roman font according to Springer's eBook style:
+% \renewcommand\UrlFont{\color{blue}\rmfamily}
 \usepackage[english]{babel}
@@
 \usepackage[T1]{fontenc}
-\usepackage{authblk}
 \usepackage[export]{adjustbox}
@@
 \usepackage{ae,aecompl}
-%% Sets page size and margins
-\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
 
@@
 \usepackage{wrapfig}
-\usepackage{amsthm}
-\usetikzlibrary{arrows,automata}
+%\usepackage{amsthm}
 \usepackage{algpseudocode}
@@
 \usepackage{caption}
-\usepackage{subcaption}
 \usepackage{listings}
@@
 \definecolor{purple}{rgb}{0.65, 0.12, 0.82}
-\floatname{algorithm}{Procedure}
-\renewcommand{\algorithmicrequire}{\textbf{Input:}}
-\renewcommand{\algorithmicensure}{\textbf{Output:}}
-
-\lstdefinelanguage{JavaScript}{
-	keywords={typeof, contract, struct, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
-	keywordstyle=\color{blue}\bfseries,
-	ndkeywords={class, export, boolean, throw, implements, import, this},
-	ndkeywordstyle=\color{darkgray}\bfseries,
-	identifierstyle=\color{black},
-	sensitive=false,
-	comment=[l]{//},
-	morecomment=[s]{/*}{*/},
-	commentstyle=\color{purple}\ttfamily,
-	stringstyle=\color{red}\ttfamily,
-	morestring=[b]',
-	morestring=[b]"
-}
-
-\lstset{
-	language=JavaScript,
-	backgroundcolor=\color{lightgray},
-	extendedchars=true,
-	basicstyle=\footnotesize\ttfamily,
-	showstringspaces=false,
-	showspaces=false,
-	numbers=left,
-	numberstyle=\footnotesize,
-	numbersep=9pt,
-	tabsize=2,
-	breaklines=true,
-	showtabs=false,
-	captionpos=b
-}
-
-\usepackage{graphicx}
-\usepackage[
-n,
-operators,
-advantage,
-sets,
-adversary,
-landau,
-probability,
-notions,	
-logic,
-ff,
-mm,
-primitives,
-events,
-complexity,
-asymptotics,
-keys]{cryptocode}
-\usepackage[colorinlistoftodos]{todonotes}
-\usepackage[colorlinks=true, allcolors=blue]{hyperref}
-
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-
-\newcommand{\Mod}[1]{\ (\mathrm{mod}\ #1)}
 
@@
 
-\DeclareMathOperator{\EX}{\mathbb{E}}% expected value
-\providecommand{\keywords}[1]{\textbf{\textit{Keywords:}} #1}
-
-\renewcommand{\lstlistingname}{Figure}% Listing -> Algorithm
-\renewcommand{\lstlistlistingname}{List of \lstlistingname s}% List of Listings -> List of Algorithms
-
-\newcommand{\smallsim}{\smallsym{\mathrel}{\sim}}
-
-\makeatletter
-\newcommand{\smallsym}[2]{#1{\mathpalette\make@small@sym{#2}}}
-\newcommand{\make@small@sym}[2]{%
-	\vcenter{\hbox{$\m@th\downgrade@style#1#2$}}%
-}
-\newcommand{\downgrade@style}[1]{%
-	\ifx#1\displaystyle\scriptstyle\else
-	\ifx#1\textstyle\scriptstyle\else
-	\scriptscriptstyle
-	\fi\fi
-}
-\makeatother
-
-\title{Topological Analysis of Bitcoin's Lightning Network }
-\author[1]{István András Seres}
-\author[1]{László Gulyás}
-\author[1]{Dániel A. Nagy}
-\author[1]{Péter Burcsi}
-\affil[1]{Department of Computer Algebra, Eötvös Loránd University}
 \begin{document}
-\maketitle
-
+%
+\title{Topological Analysis of Bitcoin's Lightning Network}
+%
+%\titlerunning{Abbreviated paper title}
+% If the paper title is too long for the running head, you can set
+% an abbreviated paper title here
+%
+\author{István András Seres\inst{1} \and
+László Gulyás\inst{1} \and
+Dániel A. Nagy\inst{1} \and
+Péter Burcsi\inst{1}}
+%
+\authorrunning{I.A. Seres et al.}
+% First names are abbreviated in the running head.
+% If there are more than two authors, 'et al.' is used.
+%
+\institute{Eötvös Loránd University, Budapest 1053, HUN
+\\
+\email{\{seris,lagu,nagyda,bupe\}@inf.elte.hu}}
+%
+\maketitle              % typeset the header of the contribution
+%
 \begin{abstract}
@@
 In this paper, we quantify the structural properties of LN and argue that LN's current topological properties can be ameliorated in order to improve the security of LN, enabling it to reach its true potential.
+
+\keywords{Bitcoin \and Lightning Network \and Network Security \and Network Topology \and Payment Channel Network \and Network Robustness.}
 \end{abstract}
-\keywords{Bitcoin, Lightning Network, Network Security, Network Topology, Payment Channel Network, Network Robustness}
-
-\section{Introduction}
-Recently the Bitcoin \cite{nakamoto2008bitcoin} network celebrated its 10th anniversary.
-During these years Bitcoin gained a huge popularity due to its publicly verifiable, decentralized, permissionless and censorship-resistant nature.
+%
+%
+%
+Since its launch, Bitcoin \cite{nakamoto2008bitcoin} gained a huge popularity due to its publicly verifiable, decentralized, permissionless and censorship-resistant nature.
 This tremendous popularity and increasing interest in Bitcoin pushed its network's throughput to its limits.
@@
 
-\begin{wrapfigure}{r}{0.6\textwidth}
-	\captionsetup{justification=centering,margin=0.5cm}
-	\begin{center}
-		\includegraphics[width=0.9\textwidth]{LNtopology.png}
-	\end{center}
-
-	\caption{LN's topology. Nodes with higher degree are highlighted with lighter colors and larger circles.}\label{fig:lntopology}
-	\vspace{-10pt}
-\end{wrapfigure}
-
 To alleviate these scalability issues the Lightning Network (LN) was designed in 2016 \cite{poon2016bitcoin}, and launched in 2018, January.
 The main insight of LN is that transactions can be issued off-blockchain in a trust-minimized manner achieving instant transaction confirmation times with negligible fees, whilst retaining the security of the underlying blockchain.
-
 Bidirectional payment channels can be formed on-chain using a construction called Hashed Timelock Contracts (HTLC).
@@
 \section{Lightning Network's Topology}
-\begin{wrapfigure}[20]{r}{5.5cm}
+\begin{wrapfigure}[21]{r}{6.5cm}
 	\begin{tabular}{ | l | c | }
@@
 
-\begin{wrapfigure}{r}{0.6\textwidth}
+\begin{wrapfigure}{r}{0.7\textwidth}	
+		\includegraphics[width=0.8\textwidth]{degreehistogramloglogscale.png}
 	\caption{LN's degree distribution}\label{fig:degreedist}	
-	\begin{center}
-		\includegraphics[width=0.85\textwidth]{degreehistogramloglogscale.png}
-	\end{center}	
 \end{wrapfigure}
 
-Negative degree assortativity of the graph indicates that on average low degree nodes tend to connect to high degree nodes rather than low degree nodes \cite{newman2002assortative}.
+Negative degree assortativity of the graph indicates that on average low degree nodes tend to connect to high degree nodes rather than low degree nodes.
 Such a dissortative property hints a hub and spoke network structure, which is also reflected in the degree distribution, see Figure~\ref{fig:degreedist}.
@@
 
-\begin{figure}[h]
-	\centering
-	\begin{minipage}{.6\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{betweennessCentrality.png}
-		\captionof{figure}{LN's betweenness centrality}
-		\label{fig:betweennescentrality}
-	\end{minipage}%
-	\begin{minipage}{.6\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{closenessCentrality.png}
-		\captionof{figure}{LN's closeness centrality}
-		\label{fig:closenesscentrality}
-	\end{minipage}
-\end{figure}
-
 Small-world architectures, like LN, exhibit high clustering with short path lenghts.
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{clusteringCoefficient.png}
-	\caption{Local clustering coefficient of LN}\label{fig:localclustering}
-\end{figure}
-
 LN's local clustering coefficient distribution suggestively captures that LN is essentially comprised of a small central clique and a loosely connected periphery.
@@
 \subsection{Analysis of LN's degree distribution}
+
+\begin{wrapfigure}{r}{0.7\textwidth}
+	\includegraphics[width=0.75\textwidth]{clusteringCoefficient.png}
+	\caption{Local clustering coefficient of LN}\label{fig:localclustering}
+\end{wrapfigure}
 
@@
 Majority of nodes have very few payment channels, although there are a few hubs who have significantly more connections as it can be seen in Figure~\ref{fig:degreedist}.
-
 The scale-freeness of LN is further justified also by applying the method introduced in \cite{clauset2009power}.
@@
 \subsection{Random Failures}
-\begin{wrapfigure}[16]{r}{5.5cm}
+\begin{wrapfigure}[16]{r}{5cm}
 	\begin{tabular}{ | l | c | }
@@
 
-\newpage
 \subsection{Targeted attacks}
@@
 	\centering
-	\begin{minipage}{.6\textwidth}
+	\begin{minipage}{.5\textwidth}
 		\centering
@@
 	\end{minipage}%
-	\begin{minipage}{.6\textwidth}
+	\begin{minipage}{.5\textwidth}
 		\centering
@@
 
-\begin{wrapfigure}[21]{r}{5.5cm}
-	\caption{Real networks under targeted attacks. Values of critical thresholds for other real networks are taken from \cite{barabasi2016network} and \cite{lin2017assessing}.}\label{fig:randfailures}
+\begin{wrapfigure}[17]{r}{5cm}
 	\begin{tabular}{ | l | c | }
@@
 	\end{tabular}
+	\caption{Real networks under targeted attacks. Values of critical thresholds for other real networks are taken from \cite{barabasi2016network} and \cite{lin2017assessing}.}\label{fig:randfailures}
 \end{wrapfigure}
@@
 
-\begin{wrapfigure}{r}{0.7\textwidth}
-	\captionsetup{justification=centering,margin=0.1cm}
-	\caption{High degree removal (HDR) attack effects average shortest path lengths}\label{fig:attackeffectpath}
-	\begin{center}
+\begin{figure}[h]
+	\centering
+	\begin{minipage}{.5\textwidth}
+		\centering
 		\includegraphics[width=\linewidth]{attackEffectPathLength.png}
-	\end{center}
-\end{wrapfigure}
+		\captionof{figure}{High degree removal (HDR) attack effects average shortest path lengths}\label{fig:attackeffectpath}
+	\end{minipage}%
+	\begin{minipage}{.5\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{randomHighBetweenness.png}
+		\captionof{figure}{Percolation thresholds for various attack scenarios: $f_{c}^{HDR}=0.1627$, $f_{c}^{HBR}=0.1409$, $f_{c}^{RND}=0.9645$}\label{fig:randhighbetween}
+	\end{minipage}
+\end{figure}
 
@@
 This could cause increased ratio of failed payments due to larger payment routes.
-
-\begin{figure}{r}
-	\captionsetup{justification=centering,margin=0.5cm}
-	\begin{center}
-		\includegraphics[width=\linewidth]{randomHighBetweenness.png}	
-	\end{center}	
-	\caption{Percolation thresholds for various attack scenarios: $f_{c}^{HDR}=0.1627$, $f_{c}^{HBR}=0.1409$, $f_{c}^{RND}=0.9645$}\label{fig:randhighbetween}
-	\vspace{-10pt}
-\end{figure}
 
@@
 This could be achieved by LN client implementations by implicitly mandating newcomers to connect to not only hubs, as current implementations do, but also to at least a few random nodes.
-This would largely increase robustness of LN even against targeted attacks.
 
@@
 LN is well approximated by the scale-free model and also its attack tolerance properties are similar to those of scale-free networks; in particular, while LN is robust against random failures, it is quite vulnerable in the face of targeted attacks.
-High-level depictions of LN's topology, like Figure~\ref{fig:lntopology}, convey a false image of security and robustness.
+High-level depictions of LN's topology convey a false image of security and robustness.
 As we have demonstrated, LN is structurally weak against rational adversaries.
@@
 We are grateful for the insightful comments and discussions to Chris Buckland, Daniel Goldman, Olaoluwa Osuntokun and Alex Bosworth.
+%
+% ---- Bibliography ----
+%
+% BibTeX users should specify bibliography style 'splncs04'.
+% References will then be sorted and formatted in the correct style.
+%
+% \bibliographystyle{splncs04}
+% \bibliography{sample}
+%
+\begin{thebibliography}{10}
 
-\bibliographystyle{plain}
-\bibliography{sample}
+	\bibitem{barabasi2016network}
+	Albert-L{\'a}szl{\'o} Barab{\'a}si et~al.
+	\newblock {\em Network science}.
+	\newblock Cambridge university press, 2016.
 
+	\bibitem{clauset2009power}
+	Aaron Clauset, Cosma~Rohilla Shalizi, and Mark~EJ Newman.
+	\newblock Power-law distributions in empirical data.
+	\newblock {\em SIAM review}, 51(4):661--703, 2009.
+
+	\bibitem{li2005towards}
+	Lun Li, David Alderson, John~C Doyle, and Walter Willinger.
+	\newblock Towards a theory of scale-free graphs: Definition, properties, and
+	implications.
+	\newblock {\em Internet Mathematics}, 2(4):431--523, 2005.
+
+	\bibitem{lin2017assessing}
+	Yuan Lin, Wei Chen, and Zhongzhi Zhang.
+	\newblock Assessing percolation threshold based on high-order non-backtracking
+	matrices.
+	\newblock In {\em Proceedings of the 26th International Conference on World
+		Wide Web}, pages 223--232. International World Wide Web Conferences Steering
+	Committee, 2017.
+
+	\bibitem{nakamoto2008bitcoin}
+	Satoshi Nakamoto.
+	\newblock Bitcoin: A peer-to-peer electronic cash system.
+	\newblock 2008.
+
+	\bibitem{poon2016bitcoin}
+	Joseph Poon and Thaddeus Dryja.
+	\newblock The bitcoin lightning network: Scalable off-chain instant payments.
+	\newblock {\em See https://lightning. network/lightning-network-paper. pdf},
+	2016.
+
+	\bibitem{roos2017settling}
+	Stefanie Roos, Pedro Moreno-Sanchez, Aniket Kate, and Ian Goldberg.
+	\newblock Settling payments fast and private: Efficient decentralized routing
+	for path-based transactions.
+	\newblock {\em arXiv preprint arXiv:1709.05748}, 2017.
+
+	\bibitem{shargel2003optimization}
+	Benjamin Shargel, Hiroki Sayama, Irving~R Epstein, and Yaneer Bar-Yam.
+	\newblock Optimization of robustness and connectivity in complex networks.
+	\newblock {\em Physical review letters}, 90(6):068701, 2003.
+
+	\bibitem{watts1998collective}
+	Duncan~J Watts and Steven~H Strogatz.
+	\newblock Collective dynamics of ‘small-world’networks.
+	\newblock {\em nature}, 393(6684):440, 1998.
+
+\end{thebibliography}
 \end{document}

### 2019-04-14 article/Springer/LNTopology.tex
Final Springer Version of the article

@@
 %
-\author{István András Seres\inst{1} \and
+\author{István András Seres\inst{1}\orcidID{0000-0003-0143-4057} \and
 László Gulyás\inst{1} \and
 Dániel A. Nagy\inst{1} \and
-Péter Burcsi\inst{1}}
+Péter Burcsi\inst{1}\orcidID{0000-0003-3306-6500}}
 %
@@
 \\
-\email{\{seris,lagu,nagyda,bupe\}@inf.elte.hu}}
+\email{istvanseres@caesar.elte.hu,gulyahps.elte.hu,nagy.da@gmail.com,bupe@inf.elte.hu}}
 %
@@
 %
-Since its launch, Bitcoin \cite{nakamoto2008bitcoin} gained a huge popularity due to its publicly verifiable, decentralized, permissionless and censorship-resistant nature.
+Since its launch, Bitcoin~\cite{nakamoto2008bitcoin} gained a huge popularity due to its publicly verifiable, decentralized, permissionless and censorship-resistant nature.
 This tremendous popularity and increasing interest in Bitcoin pushed its network's throughput to its limits.
 Without further advancements, the Bitcoin network can only settle $7$ transactions per second (tps), while mainstream centralized payment providers such as Visa and Mastercard can process approximately \num[group-separator={,}]{40000} tps in peak hours.
-Moreover one might need to pay large transaction fees on the Bitcoin network, while also need to wait 6 new blocks to be published in order to be certain enough that the transaction is included in the blockchain.
+Moreover one might need to pay large transaction fees on the Bitcoin network, while also need to wait 6 new blocks ($\sim 1$ hour) to be published in order to be certain enough that the transaction is included in the blockchain.
 
@@
 Using these payment channels as building blocks one might establish a payment channel network, where it is not necessary to have direct payment channels between nodes to transact with each other, but they could simply route their payments through other nodes' payment channels.
-Such a network can be built, because LN achieves payments to be made without any counterparty risk, however efficient and privacy-preserving payment routing remains a challenging algorithmic task \cite{roos2017settling}.
+Such a network can be built, because LN achieves payments to be made without any counterparty risk, however efficient and privacy-preserving payment routing remains a challenging algorithmic task~\cite{roos2017settling}.
 
@@
 These findings suggest that LN's topology can be ameliorated in order to achieve its true potential.
-\section{Lightning Network's Topology}
+\section{Background on Lightning Network}
+In this section we provide a short recap on how LN works.
+In the following we will use the terms Layer-2 and off-chain interchangeably.
+LN is a so-called Layer-2 technology, which allows participants issuing transactions without sending a Layer-1 transaction on the Bitcoin parent chain.
+All parties cooperatively
+open a channel by locking collateral on the blockchain.
+The funds can only be released by unanimous agreement or through a pre-defined refund condition~\cite{cryptoeprint:2019:360}.
+One of the greatest challenge of Layer-2 technologies is to solve how participants can agree on new state updates in a trustless or trust-minimized manner.
+
+Let's take the following toy example: Alice and Bob creates by a single Layer-1 transaction a payment channel with initial balances $10\bitcoinA$ and $0\bitcoinA$ respectively.
+Straightaway Alice can issue off-chain transactions to Bob up to $10\bitcoinA$.
+Let's assume Alice issued $3$ off-chain transactions to Bob each worth of $1\bitcoinA$.
+Afterwards Alice's and Bob's balance should be $7\bitcoinA$ and $3\bitcoinA$ and neither Alice, nor Bob should be able to redeem previous balances on the parent chain.
+LN achieves this by a replace by revocation mechanism, namely both parties collectively
+authorize a new state before revoking the previous state.
+Upon dispute, the blockchain provides a time period for
+parties to prove that the published state is a revoked state \cite{cryptoeprint:2019:360}.
+Revoking old channel states is achieved by the exchange of revocation secrets.
+These secrets, hash preimages, are needed to be retained during the channel's lifetime.
+A penalty mechanism
+discourages parties from broadcasting older states. If one party
+broadcasts a revoked state, the blockchain accepts within a
+time-window proofs of maleficence from the other party. A
+successful dispute allots the winning party \textit{all} coins of the
+channel.
+In our example if Alice broadcasts a revoked channel state with balances $8\bitcoinA$ and $2\bitcoinA$, Bob can prove, that Alice maliciously broadcasted a revoked state.
+The penalty mechanism grants all the $10\bitcoinA$ to Bob.
+
+The great insight of LN, is that if now Alice would like to issue a payment to Cecily, who eventually has already established a payment channel to Bob, then Alice does not need to open a payment channel and create a costly on-chain transaction, rather she can route her payment through her payment channel with Bob to Cecily.
+However the maximum amount of bitcoins Alice can send to Cecily is the minimum of all the individual balances on the payment route from Alice to Cecily.
+Hashed time-locked contracts (HTLC) enable routed payments to be atomic.
+For a technical description of HTLCs and multi-hop payments the astute reader is referred to~\cite{poon2016bitcoin}.
+
+In the following we will model LN as an undirected, weighted graph, where nodes are entities who can issue payments using payment channels which are the edges of the LN graph.
+The weight on the edges, capacities, are the sum of individual balances.
+Note, that in most cases individual balances are not known to outsiders.
+Only the capacity of a payment channel is public information, however one can effectively assess individual balances with handy algorithms~\cite{cryptoeprint:2019:328}.
+
+\section{Lightning Network's Topology}\label{lntopology}
 \begin{wrapfigure}[21]{r}{6.5cm}
-	\begin{tabular}{ | l | c | }
+	\begin{tabular}{| l | c |}
 		\hline
@@
 The closer to $1$  s-metric of $G$ is, the more scale-free the network.
-Diameter and radius of LN suggests that LN is a small world.
+Diameter and radius of LN suggest that LN is a small world.
 Somewhat scale-freeness is also exhibited in the degree distribution of LN.
@@
 
-\begin{wrapfigure}[17]{r}{5cm}
+\begin{wrapfigure}[19]{r}{5cm}
 	\begin{tabular}{ | l | c | }
@@
 	\end{tabular}
-	\caption{Real networks under targeted attacks. Values of critical thresholds for other real networks are taken from \cite{barabasi2016network} and \cite{lin2017assessing}.}\label{fig:randfailures}
+	\caption{Real networks under targeted attacks.
+Values of critical thresholds for other real networks are taken from \cite{barabasi2016network} and \cite{lin2017assessing}.}\label{fig:targetedfailures}
 \end{wrapfigure}
@@
 		\centering
-		\includegraphics[width=\linewidth]{randomHighBetweenness.png}
-		\captionof{figure}{Percolation thresholds for various attack scenarios: $f_{c}^{HDR}=0.1627$, $f_{c}^{HBR}=0.1409$, $f_{c}^{RND}=0.9645$}\label{fig:randhighbetween}
+		\includegraphics[width=\linewidth]{lostCapacity.png}
+		\captionof{figure}{Lost capacity as removing high-degree nodes}\label{fig:lostCapacity}
 	\end{minipage}
@@
 
-Node outage not only affects robustness and connectivity properties, but also affects average shortest path lengths.
+Node outage not only affects robustness and connectivity properties, but also affects average shortest path lengths and available liquidity.
 Although the outage of random nodes does not significantly increase the average shortest path lengths in LN, targeted attacks against hubs increase distances between remaining nodes.
-The spillage of high-degree nodes not only decrease the amount of available liquidity but also rapidly increase the necessary hops along payment routes as Figure~\ref{fig:attackeffectpath} suggests.
-This could cause increased ratio of failed payments due to larger payment routes.
+The spillage of high-degree nodes not only decreases the amount of available liquidity but also rapidly increases the necessary hops along payment routes as Figure~\ref{fig:attackeffectpath} and ~\ref{fig:lostCapacity} suggest.
+This could cause increased ratio of failed payments due to larger payment routes and sparser liquidity.
+Figure~\ref{fig:lostCapacity} demonstrates how capital allocation is centred upon a few high degree nodes, namely already the removal of as few nodes as $37$ decreases the available liquidity by more than $50\%$.
+Unfortunately most of these nodes are run by a handful of companies.
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\linewidth]{randomHighBetweenness.png}
+	\captionof{figure}{Percolation thresholds for various attack scenarios: $f_{c}^{HDR}=0.1627$, $f_{c}^{HBR}=0.1409$, $f_{c}^{RND}=0.9645$}\label{fig:randhighbetween}
+\end{figure}
 
 \subsection{Improving LN's resilience against random failures and attacks}
-Designing networks which are robust to random failures and targeted attacks appear to be a conflicting desire \cite{barabasi2016network}.
+Designing networks which are robust to random failures and targeted attacks appear to be a conflicting desire~\cite{barabasi2016network}.
 For instance a star graph, the simplest hub and spoke network, is resilient to random failures.
@@
 
-A similar optimization strategy of robustness and connectivity to that of \cite{shargel2003optimization} could be applied to LN as well.
-We leave it for future work to empirically assess the robustness and connectivity gains if strategy of \cite{shargel2003optimization} would be implemented in LN client implementations.
+A similar optimization strategy of robustness and connectivity to that of~\cite{shargel2003optimization} could be applied to LN as well.
+We leave it for future work to empirically assess the robustness and connectivity gains if the strategy of~\cite{shargel2003optimization} would be implemented in LN client implementations.
 
@@
 Thus, to provide robust Layer-2 solutions for blockchains, such as LN and Raiden, the community needs to aim at building resilient network topologies.
-\section{Acknowledgements}
+\paragraph{\textbf{Acknowledgements.}}
 We are grateful for the insightful comments and discussions to Chris Buckland, Daniel Goldman, Olaoluwa Osuntokun and Alex Bosworth.
+Furthermore we are thankful for Altangent Labs\footnote{\url{https://www.blocktap.io/}} for providing us the invaluable data.
+The research at Eötvös Loránd University was partially supported by the European Union, co-financed by the European Social Fund (EFOP-3.6.2-16-2017-00012).
 %
@@
 %
-% \bibliographystyle{splncs04}
-% \bibliography{sample}
-%
-\begin{thebibliography}{10}
-
-	\bibitem{barabasi2016network}
-	Albert-L{\'a}szl{\'o} Barab{\'a}si et~al.
-	\newblock {\em Network science}.
-	\newblock Cambridge university press, 2016.
-
-	\bibitem{clauset2009power}
-	Aaron Clauset, Cosma~Rohilla Shalizi, and Mark~EJ Newman.
-	\newblock Power-law distributions in empirical data.
-	\newblock {\em SIAM review}, 51(4):661--703, 2009.
-
-	\bibitem{li2005towards}
-	Lun Li, David Alderson, John~C Doyle, and Walter Willinger.
-	\newblock Towards a theory of scale-free graphs: Definition, properties, and
-	implications.
-	\newblock {\em Internet Mathematics}, 2(4):431--523, 2005.
-
-	\bibitem{lin2017assessing}
-	Yuan Lin, Wei Chen, and Zhongzhi Zhang.
-	\newblock Assessing percolation threshold based on high-order non-backtracking
-	matrices.
-	\newblock In {\em Proceedings of the 26th International Conference on World
-		Wide Web}, pages 223--232. International World Wide Web Conferences Steering
-	Committee, 2017.
-
-	\bibitem{nakamoto2008bitcoin}
-	Satoshi Nakamoto.
-	\newblock Bitcoin: A peer-to-peer electronic cash system.
-	\newblock 2008.
-
-	\bibitem{poon2016bitcoin}
-	Joseph Poon and Thaddeus Dryja.
-	\newblock The bitcoin lightning network: Scalable off-chain instant payments.
-	\newblock {\em See https://lightning. network/lightning-network-paper. pdf},
-	2016.
-
-	\bibitem{roos2017settling}
-	Stefanie Roos, Pedro Moreno-Sanchez, Aniket Kate, and Ian Goldberg.
-	\newblock Settling payments fast and private: Efficient decentralized routing
-	for path-based transactions.
-	\newblock {\em arXiv preprint arXiv:1709.05748}, 2017.
-
-	\bibitem{shargel2003optimization}
-	Benjamin Shargel, Hiroki Sayama, Irving~R Epstein, and Yaneer Bar-Yam.
-	\newblock Optimization of robustness and connectivity in complex networks.
-	\newblock {\em Physical review letters}, 90(6):068701, 2003.
-
-	\bibitem{watts1998collective}
-	Duncan~J Watts and Steven~H Strogatz.
-	\newblock Collective dynamics of ‘small-world’networks.
-	\newblock {\em nature}, 393(6684):440, 1998.
-
-\end{thebibliography}
+\newpage
+\bibliographystyle{splncs04}
+\bibliography{sample}
 \end{document}

### 2019-04-14 parseGraph.py

@@ -2,10 +2,12 @@ import networkx as nx
 import json
 from pprint import pprint
 import math
+from matplotlib import mlab
 import matplotlib.pyplot as plt
 import matplotlib.colors as mcolors
 import matplotlib.ticker as mticker
 import random
+import types
 import operator
 from matplotlib.ticker import MaxNLocator
 import collections
@@ -23,14 +25,30 @@ from networkx.algorithms import approximation
 allMoneyStaked = 0
 allWeights = []
 
+def defineGraph(data) -> object:
+    global allMoneyStaked
+    G = nx.Graph()
+    for x in range(len(data)):
+        G.add_edge(data[x]['node2_pub'], data[x]['node1_pub'], capacity=data[x]['capacity'])
+        allWeights.append(int(data[x]['capacity']))
+        allMoneyStaked+=int(data[x]['capacity'])
+    return G
+
+
+##https://graph.lndexplorer.com/api/graph
+def readFile() -> object:
+    with open('graph.json') as f:
+        data = json.load(f)
+    return data['edges']
+
 def main():
-    G=defineGraph(readFile())
+    G = defineGraph(readFile())
     degree_sequence = sorted([d for n, d in G.degree()], reverse=True)  # degree sequence
     # print "Degree sequence", degree_sequence
     degreeCount = collections.Counter(degree_sequence)
     deg, cnt = zip(*degreeCount.items())
 
-    basicStatistics(G)
+    #basicStatistics(G)
     #degreeDistribution(G) #percentile graph needs to be added
     #weightsDistribution(G)
     #shortestPaths(G)
@@ -47,7 +65,72 @@ def main():
     #attackingBetweenness(G,deg, cnt)
     #attackingHighDegrees(G)
     #drawHistogram(G)
-    improvingRobustness(G)
+    #improvingRobustness(G)
+    edgeCapacityDistributions(G)
+
+def edgeCapacityDistributions(G):
+    richestStakers = {}
+    for n in G.nodes():
+        capacityOfn = 0
+        for m in G.neighbors(n):
+            capacityOfn += int(G[n][m]['capacity'])
+        richestStakers[n]=capacityOfn
+    sortedStakers = list(sorted(richestStakers.items(), key=operator.itemgetter(1), reverse=True))
+    sortedCapacities = []
+    for i in sortedStakers:
+        sortedCapacities.append(i[1])
+
+    lostCapacityPercentage = []
+    lostCapacities = []
[…]

### 2019-04-18 parseGraph.py
New snapshot for Claas

@@ -37,7 +37,7 @@ def defineGraph(data) -> object:
 
 ##https://graph.lndexplorer.com/api/graph
 def readFile() -> object:
-    with open('graph.json') as f:
+    with open('graph20190418.json') as f:
         data = json.load(f)
     return data['edges']
 
@@ -48,7 +48,7 @@ def main():
     degreeCount = collections.Counter(degree_sequence)
     deg, cnt = zip(*degreeCount.items())
 
-    #basicStatistics(G)
+    basicStatistics(G)
     #degreeDistribution(G) #percentile graph needs to be added
     #weightsDistribution(G)
     #shortestPaths(G)
@@ -66,7 +66,7 @@ def main():
     #attackingHighDegrees(G)
     #drawHistogram(G)
     #improvingRobustness(G)
-    edgeCapacityDistributions(G)
+    #edgeCapacityDistributions(G)
 
 def edgeCapacityDistributions(G):
     richestStakers = {}
@@ -391,19 +391,20 @@ def basicStatistics(G):
     print("LN degree assortativity",nx.algorithms.assortativity.degree_assortativity_coefficient(G))
     #print("LN rich-club coefficient: ", nx.algorithms.richclub.rich_club_coefficient(G))
     #print("LN rich-club normalized coefficient: ", nx.algorithms.richclub.rich_club_coefficient(G, normalized=True))
-    #print(list(nx.connected_components(G))[1])
     G.remove_nodes_from(list(nx.connected_components(G))[1]) #there is a small second component
+    G.remove_nodes_from(list(nx.connected_components(G))[2])  # there is a small second component
+    G.remove_nodes_from(list(nx.connected_components(G))[1])  # there is a small second component
     #print("LN diameter: ", nx.algorithms.distance_measures.diameter(G)) #6
     #print("LN radius", nx.algorithms.distance_measures.radius(G)) #3
     #print("LN Wiener index", nx.algorithms.wiener_index(G)) #7686159.0
-    print("LN is Eulerian: ",nx.algorithms.is_eulerian(G))
-    print("LN is planar: ", nx.algorithms.planarity.check_planarity(G))
-    print("Number of isolates in LN: ", list(nx.isolates(G)))
+    #print("LN is Eulerian: ",nx.algorithms.is_eulerian(G))
+    #print("LN is planar: ", nx.algorithms.planarity.check_planarity(G))
+    #print("Number of isolates in LN: ", list(nx.isolates(G)))
[…]
